---
title: "Best NWP FINAL"
author: "Eirik Sjåvik"
date: "2023-03-06"
output: html_document
---


#This document contains information about chapter 7: Use of NWP Forecasts for Temperature prediction

It contains model runs from: 
1) Out of sample Climatology
2) In sample Climatology for 0.1-0.9 quantiles
3) Weighted NWP-quantile models for 0.1-0.9 (Non-regression)
- Comparison plot
- Skill plot
4) Quantile regression models
- Time Covariates
- All lead_time models
- Daily models

5) Spline alternative to regression models
- 
6) Scoring Intervals

# Load data
```{r, cache = TRUE}
library(DemandForecast)
# library(data.table)
# library(ncdf4)
# library(parallel)
# library(mgcv)
# library(quantreg)

ERA_NWP = get_ERA_NWP(ERA_path = "/mn/kadingir/datascience_000000/eirikhsj/PC_ERA_79_92.Rda", 
                      NWP_path ="/mn/kadingir/datascience_000000/eirikhsj/NWP_quant_1993_2023.Rda",
                      quant = "90", reweight = FALSE)

ERA_NWP[, season:= ifelse(month(date) %in% c(12,1,2), 1, 
                            ifelse(month(date) %in% c(3,4,5), 2,
                            ifelse(month(date) %in% c(6,7,8), 3, 4)))]
```


# 1) Weighted vs Quantile regression Climatology 0.9
```{r}
ERA_NWP[,raw_loss := pinball_loss(0.9, NWP1_90, PC1)]
#ERA_NWP[,mean(raw_loss)]
plot(ERA_NWP[,mean(raw_loss), keyby = lead_time], type = 'l', ylim = c(0, 13))
lines(Mod_9_120_NWP1_check_climat$Results[,mean(test_loss), by = lead_time],col = 'red')
#lines(TTTT$Results[,mean(test_loss), keyby = lead_time], col = 'purple')
legend('bottomright', col = c('black','red', 'purple'), title = 'Model', legend = c('NWP1 (Weighted /direct)', 'NWP1 (Qreg All data)', "NWP1 (Qreg 6-hour Beta)"), pch = 16, lty = 1)
```

### Plot of Weighted quantile estimate for specific month
```{r}
#load("~/Desktop/Master2023/Data/ERA_NWP_raw_loss.Rda")
plot_dat = ERA_NWP_raw_loss[init_date == '2020-12-01', c(paste0("NWP_PC1_q",seq(1:9),"0"), 'PC1','NWP_PC1_mean', 'hour')]
plot_dat[,x:= 1:500]
ggplot() +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = NWP_PC1_q10, ymax =NWP_PC1_q90, fill = "1-9"), alpha = 0.8) +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = NWP_PC1_q20, ymax = NWP_PC1_q80, fill = "2-8"), alpha = 0.6) +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = NWP_PC1_q30, ymax = NWP_PC1_q70, fill = "3-7"), alpha = 0.4) +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = NWP_PC1_q40, ymax = NWP_PC1_q60, fill = "4-6"), alpha = 0.2) +
    scale_fill_brewer(palette = "RdYlGn") +
    geom_line(data = plot_dat[hour == 6],  color = 'blue',aes(x = x, y = PC1))+
    geom_line(data = plot_dat[hour == 6],  color = 'black',aes(x = x, y = NWP_PC1_mean))+
    geom_line(data = plot_dat[hour == 6],  color = 'purple',aes(x = x, y = NWP_PC1_q50))+
    theme_classic()+
    coord_cartesian(ylim = c(-150, 370), xlim = c(0,500)) 
```
# Climatology models (Out-of-sample for all quantiles)
```{r}
Clima_90 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.8, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)                                            
Clima_80 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.8, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)                                              
Clima_70 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.7, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)  
Clima_60 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.6, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)                                            
Clima_50 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)                                              
Clima_40 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.4, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)                                              
Clima_30 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.3, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)                                              
Clima_20 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.2, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)
Clima_10 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.1, ERA_NWP, 0, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)

setnames(Clima_90$Results, 'clima_pred', 'clima_pred90')
setnames(Clima_80$Results, 'clima_pred', 'clima_pred80')
setnames(Clima_70$Results, 'clima_pred', 'clima_pred70')
setnames(Clima_60$Results, 'clima_pred', 'clima_pred60')
setnames(Clima_50$Results, 'clima_pred', 'clima_pred50')
setnames(Clima_40$Results, 'clima_pred', 'clima_pred40')
setnames(Clima_30$Results, 'clima_pred', 'clima_pred30')
setnames(Clima_20$Results, 'clima_pred', 'clima_pred20')
setnames(Clima_10$Results, 'clima_pred', 'clima_pred10')

Clima = Clima_10$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred10)]
Clima = merge(Clima, Clima_20$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred20)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
Clima = merge(Clima, Clima_30$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred30)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
Clima = merge(Clima, Clima_40$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred40)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
Clima = merge(Clima, Clima_50$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred50)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
Clima = merge(Clima, Clima_60$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred60)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
Clima = merge(Clima, Clima_70$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred70)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
Clima = merge(Clima, Clima_80$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred80)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
Clima = merge(Clima, Clima_90$Results[,.(date, hour, month_day, PC1, init_date, lead_time, clima_pred90)], by = c('date', 'hour', 'init_date', 'PC1', 'lead_time', 'month_day'))
```

### Comparison of Wegihted NWP1 with Climatology at different quantiles 0.1-0.9
```{r}
pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/NWP_WQE_pin_score.pdf", height = 7, width = 9, pointsize = 12)

ERA_NWP_raw_loss[,'lead_time':= ((as.integer(difftime(date, init_date, units = 'days')))*4)+ hour/6]

#plot(ERA_NWP_raw_loss[, mean(pinball_loss(i/10,NWP_PC1_mean , PC1)), by = lead_time], type = 'l', ylim = c(0, 25))
colz = c('red', 'blue', 'green', 'yellow', 'brown', 'purple', 'grey', 'pink', 'orange')
colz = rep('red',9)
par(mar=c(4.5,4.5,4.5,4.5))
for (i in c(9)){
    plot(ERA_NWP_raw_loss[, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1)), by = lead_time], col = 'red', type = 'l', main = paste0('Pinball Loss and Skill Score of NWP WQE (0.', i," quantile)"), xaxt = 'n',ylab = 'Pinball Loss', xlab = 'Lead Time (Days after Forecast Initialization)', ylim = c(0, 13))
    lines(Clima[, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1)), by = lead_time], col = 'blue')
    par(new = TRUE)
    plot(1 - (ERA_NWP_raw_loss[, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1)), by = lead_time][,V1]/Clima[, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1)), by = lead_time][,V1]), type = 'l', axes = FALSE, xlab = "", ylab = "", ylim = c(-0.15, 0.75))
    axis(side = 4, at = seq(-0.1, 1, by = 0.2))
    abline(h = 0, lty = 2, col = 'black')
    abline(h = 0.1, lty = 2, col = 'grey')
    abline(h = -0.1, lty = 2, col = 'grey')
    if (ERA_NWP_raw_loss[, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1)), by = lead_time][500,V1]>17){
        l = 'right'
    } else{ l = 'topright'}
    legend(l, col = c('red', 'blue', 'black'), title = paste0("Performance at q = ", i/10), legend =  c(paste0("NWP WQE"), paste0("Climatology"), "Skill Score NWP"),pch = 16,lty = c(1))
    mtext("Skill Score", side = 4, line = 3, cex = 1)
    axis(side = 1, at = c(0,100-2,200-2,300-2,400-2,500-2), labels = c(0,25,50,75,100,125))

    point1 = which(1 - (ERA_NWP_raw_loss[, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1)), by = lead_time][,V1]/Clima[, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1)), by = lead_time][,V1])<0.1)[1]
    point0 = which(1 - (ERA_NWP_raw_loss[, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1)), by = lead_time][,V1]/Clima[, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1)), by = lead_time][,V1])<0)[1]
    #print(c(point1, point0))
    abline(v = point1, col = 'grey', lty = 2)
    abline(v =point0 , col = 'grey', lty = 2)
    text(x = 4*6, y = 0.75, labels = paste0("Day ", ceiling(point1/4)))
    text(x = 4*30, y = 0.7, labels = paste0("Day ", ceiling(point0/4)))
    # print(c(Clima[lead_time %in% 1:120, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1))],
    #           ERA_NWP_raw_loss[lead_time %in% 1:120, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1))]))
    # print(c(
    #     1 - (ERA_NWP_raw_loss[lead_time %in% 1:80, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1))]/Clima[lead_time %in% 1:80, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1))]),
    #     1 - (ERA_NWP_raw_loss[lead_time %in% 81:160, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1))]/Clima[lead_time %in% 81:160, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1))]),
    #     1 - (ERA_NWP_raw_loss[lead_time %in% 161:240, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1))]/Clima[lead_time %in% 161:240, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1))])))
    # acf(1 - (ERA_NWP_raw_loss[100:500, mean(pinball_loss(i/10, get(paste0("NWP_PC1_q",i,"0")), PC1)), by = lead_time][,V1]/Clima[100:500, mean(pinball_loss(i/10, get(paste0("clima_pred",i*10)), PC1)), by = lead_time][,V1]))
}
dev.off()
```
Looking at inter-quantile differences. 
```{r}
Clima[,dist90_10:= clima_pred90 -clima_pred10]
Clima[,mean(dist90_10), by = month(date)]
ERA_NWP_raw_loss[,dist90_10:= NWP_PC1_q90 -NWP_PC1_q10]
ERA_NWP_raw_loss[,mean(dist90_10), by = month(date)]

Clima[,dist70_30:= clima_pred70 -clima_pred30]
Clima[,mean(dist70_30), by = month(date)]
ERA_NWP_raw_loss[,dist70_30:= NWP_PC1_q70 -NWP_PC1_q30]
ERA_NWP_raw_loss[,mean(dist70_30), by = month(date)]

data.table(cbind(Clima[,mean(dist90_10), by = month(date)],ERA_NWP_raw_loss[,mean(dist90_10), by = month(date)][,V1]))


data.table(cbind(Clima[,mean(dist70_30), by = month(date)],ERA_NWP_raw_loss[,mean(dist70_30), by = month(date)][,V1]))


ERA_NWP_raw_loss[lead_time>80,mean(NWP_PC1_q90 -NWP_PC1_q10)]
Clima[lead_time>80,mean(clima_pred90 -clima_pred10)]

ERA_CLIMA = merge(Clima, ERA_NWP_raw_loss, by = c('date', 'hour', 'lead_time', 'PC1', 'init_date'))
ERA_CLIMA[, mean(clima_pred90-NWP_PC1_q90)]

```



```{r}
ERA_out_of_sample = ERA$dt_test[hour %in% c(6,12,18,24)]
ERA_out_of_sample[,month_day := format(date, format ="%m-%d")]
for (i in c(seq(0.1, 0.9, 0.1))){
    
    ERA_out_of_sample[,c(paste0("quant_",i*100)) := .(quantile(PC1,probs = i)), by = .(month_day = format(date, format ="%m-%d"), hour)]
    ERA_out_of_sample[,c(paste0("quant_",i*100,"_loss"))  := .(pinball_loss(i,get(paste0("quant_",i*100)),PC1))]
}
#ERA_correct_clima[,loss_clima := pinball_loss(0.9,quant,PC1)]

ERA_out_of_sample[year(date)==1999 & month(date) %in% c(1,2,3,4,5)]

plot_dat = ERA_out_of_sample[year(date)==2015 & month(date) %in% c(12,1,2,3,4,5), c(paste0("quant_",seq(1:9),"0"), 'PC1', 'hour')]
plot_dat = plot_dat[1:500,]
plot_dat[,x:= 1:500]
ggplot() +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = quant_10, ymax =quant_90, fill = "1-9"), alpha = 0.8) +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = quant_20, ymax = quant_80, fill = "2-8"), alpha = 0.6) +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = quant_30, ymax = quant_70, fill = "3-7"), alpha = 0.4) +
    geom_ribbon(data = plot_dat[hour == 6], aes(x = x, ymin = quant_40, ymax = quant_60, fill = "4-6"), alpha = 0.2) +
    scale_fill_brewer(type = "seq", palette = "Blues", direction = -1, guide = FALSE, na.value = "gray50") +
    geom_line(data = plot_dat[hour == 6],  color = 'blue',aes(x = x, y = PC1))+
    geom_line(data = plot_dat[hour == 6],  color = 'purple',aes(x = x, y = quant_50))+
    coord_cartesian(ylim = c(-150, 370), xlim = c(0,500)) +
    theme_classic()

```


```{r}
#rep(seq(dato, length.out = 125, by = "day"),each =4)
dato = as.Date('2013-11-01')
plot_dat2 = Clima[init_date == dato, c(paste0("clima_pred",seq(1:9),"0"), 'PC1', 'hour')]
plot_dat2[,x:= rep(seq(dato, length.out = 125, by = "day"),each =4)]
plot_dat = ERA_NWP_raw_loss[init_date == dato, c(paste0("NWP_PC1_q",seq(1:9),"0"), 'PC1','NWP_PC1_mean', 'hour')]
plot_dat[,x:= rep(seq(dato, length.out = 125, by = "day"),each =4)]
ggplot() +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred10, ymax =clima_pred90, fill = "1-9"), alpha = 0.8) +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred20, ymax = clima_pred80, fill = "2-8"), alpha = 0.6) +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred30, ymax = clima_pred70, fill = "3-7"), alpha = 0.4) +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred40, ymax = clima_pred60, fill = "4-6"), alpha = 0.2) +
        scale_fill_brewer(type = "seq", palette = "Blues", direction = -1, guide = 'none', na.value = "gray50") +
    #geom_line(data = plot_dat2[hour == 6],  color = 'purple',aes(x = x, y = clima_pred50))+
    coord_cartesian(ylim = c(-50, 320)) +
     geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q10))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q20))+
    geom_line(data = plot_dat[hour == 6], linetype = "dashed",  color = 'red',aes(x = x, y = NWP_PC1_q30))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q40))+
    geom_line(data = plot_dat[hour == 6], linetype = "dotted",  color = 'red',aes(x = x, y = NWP_PC1_q50))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q60))+
    geom_line(data = plot_dat[hour == 6], linetype = "dashed",  color = 'red',aes(x = x, y = NWP_PC1_q70))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q80))+
    geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q90))+
    geom_line(data = plot_dat2[hour == 6],  color = 'black',aes(x = x, y = PC1))+
      labs(title = "Predictive Distributions for NWP and Climatology (Winter 13/14)", x = "Date", y = "Factor Loading Value") +
    scale_x_date(date_labels = "%b-%d", breaks= c(as.Date('2013-11-01'), as.Date('2013-11-15'), as.Date('2013-12-01'), as.Date('2013-12-15'), as.Date('2014-01-01'), as.Date('2014-01-15'), as.Date('2014-02-01'), as.Date('2014-02-15'),as.Date('2014-03-01'),as.Date('2014-03-15')))+
    scale_color_manual(values = c("Line 1" = "red", "Line 2" = "blue"),
                     labels = c("Line 1", "Line 2")) +
  scale_linetype_manual(values = c("Line 1" = "solid", "Line 2" = "dashed"),
                        labels = c("Line 1", "Line 2")) +
    theme_classic()
```
```{r}
pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/Prob_forc_comp1.pdf", height = 7, width = 9, pointsize = 12)
dato = as.Date('2013-11-01')
plot_dat2 = Clima[init_date == dato, c(paste0("clima_pred",seq(1:9),"0"), 'PC1', 'hour')]
plot_dat2[,x:= rep(seq(dato, length.out = 125, by = "day"),each =4)]
plot_dat = ERA_NWP_raw_loss[init_date == dato, c(paste0("NWP_PC1_q",seq(1:9),"0"), 'PC1','NWP_PC1_mean', 'hour')]
plot_dat[,x:= rep(seq(dato, length.out = 125, by = "day"),each =4)]
ggplot() +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred10, ymax =clima_pred90, fill = "1-9"), alpha = 0.8) +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred20, ymax = clima_pred80, fill = "2-8"), alpha = 0.6) +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred30, ymax = clima_pred70, fill = "3-7"), alpha = 0.4) +
    geom_ribbon(data = plot_dat2[hour == 6], aes(x = x, ymin = clima_pred40, ymax = clima_pred60, fill = "4-6"), alpha = 0.2) +
        scale_fill_brewer(type = "seq", palette = "Blues", direction = -1, guide = 'none', na.value = "gray50") +
    #geom_line(data = plot_dat2[hour == 6],  color = 'purple',aes(x = x, y = clima_pred50))+
    coord_cartesian(ylim = c(-50, 320)) +
     geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q10))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q20))+
    geom_line(data = plot_dat[hour == 6], linetype = "dashed",  color = 'red',aes(x = x, y = NWP_PC1_q30))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q40))+
    geom_line(data = plot_dat[hour == 6], linetype = "dotted",  color = 'red',aes(x = x, y = NWP_PC1_q50))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q60))+
    geom_line(data = plot_dat[hour == 6], linetype = "dashed",  color = 'red',aes(x = x, y = NWP_PC1_q70))+
    #geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q80))+
    geom_line(data = plot_dat[hour == 6],  color = 'red',aes(x = x, y = NWP_PC1_q90))+
    geom_line(data = plot_dat2[hour == 6],  color = 'black',aes(x = x, y = PC1))+
      labs(title = "Predictive Distributions for NWP and Climatology (Winter 13/14)", x = "Date", y = "Factor Loading Value") +
    scale_x_date(date_labels = "%b-%d", breaks= c(as.Date('2013-11-01'), as.Date('2013-11-15'), as.Date('2013-12-01'), as.Date('2013-12-15'), as.Date('2014-01-01'), as.Date('2014-01-15'), as.Date('2014-02-01'), as.Date('2014-02-15'),as.Date('2014-03-01'),as.Date('2014-03-15')))+
    scale_color_manual(values = c("Line 1" = "red", "Line 2" = "blue"),
                     labels = c("Line 1", "Line 2")) +
  scale_linetype_manual(values = c("Line 1" = "solid", "Line 2" = "dashed"),
                        labels = c("Line 1", "Line 2")) +
    theme_classic()
dev.off()
```


```{r, eval  = FALSE}
# save(Mod_9_60_inter, file = 'Mod_9_60_inter.Rda')
# save(Mod_9_60_year_c, file = 'Mod_9_60_year_c.Rda')
# save(Mod_9_60_year_f, file = 'Mod_9_60_year_f.Rda')
# save(Mod_9_60_hour_c, file = 'Mod_9_60_hour_c.Rda')
# save(Mod_9_60_hour_f, file = 'Mod_9_60_hour_f.Rda')
# save(Mod_9_60_hour_sin, file = 'Mod_9_60_hour_sin.Rda')
# save(Mod_9_60_week_c, file = 'Mod_9_60_week_c.Rda')
# save(Mod_9_60_week_f, file = 'Mod_9_60_week_f.Rda')
# save(Mod_9_60_week_sin, file = 'Mod_9_60_week_sin.Rda')
# save(Mod_9_60_week_sin_2, file = 'Mod_9_60_week_sin_2.Rda')
# save(Mod_9_60_week_sin_3, file = 'Mod_9_60_week_sin_3.Rda')
# save(Mod_9_60_month_c, file = 'Mod_9_60_month_c.Rda')
# save(Mod_9_60_month_f, file = 'Mod_9_60_month_f.Rda')
# save(Mod_9_60_month_sin, file = 'Mod_9_60_month_sin.Rda')
# save(Mod_9_60_season_c, file = 'Mod_9_60_season_c.Rda')
# save(Mod_9_60_season_f, file = 'Mod_9_60_season_f.Rda')
# save(Mod_9_60_season_sin, file = 'Mod_9_60_season_sin.Rda')
# 
# save(Mod_9_60_NWP1, file = 'Mod_9_60_NWP1.Rda')
# save(Mod_9_60_NWP2, file = 'Mod_9_60_NWP2.Rda')
# save(Mod_9_60_climatology, file = 'Mod_9_60_climatology.Rda')
# 
# save(Mod_9_60_comb_a_0, file = 'Mod_9_60_comb_a_0.Rda')
# save(Mod_9_60_comb_a_1, file = 'Mod_9_60_comb_a_1.Rda') 
# save(Mod_9_60_comb_a_2, file = 'Mod_9_60_comb_a_2.Rda') 
# 
# save(Mod_9_60_int_a_0, file = 'Mod_9_60_int_a_0.Rda')
# save(Mod_9_60_int_b_0, file = 'Mod_9_60_int_b_0.Rda')
# save(Mod_9_60_int_c_0, file = 'Mod_9_60_int_c_0.Rda')
# 
# save(Mod_9_60_comb_int_c_0, file = 'Mod_9_60_comb_int_c_0.Rda')
# save(Mod_9_60_comb_int_c_1, file = 'Mod_9_60_comb_int_c_1.Rda')
# save(Mod_9_60_comb_int_c_2, file = 'Mod_9_60_comb_int_c_2.Rda')
# save(Mod_9_60_comb_int_b_0, file = 'Mod_9_60_comb_int_b_0.Rda')
# save(Mod_9_60_comb_int_b_1, file = 'Mod_9_60_comb_int_b_1.Rda')
# save(Mod_9_60_comb_int_b_2, file = 'Mod_9_60_comb_int_b_2.Rda')
# save(Mod_9_60_comb_int_a_0, file = 'Mod_9_60_comb_int_b_0.Rda')
# save(Mod_9_60_comb_int_a_1, file = 'Mod_9_60_comb_int_a_1.Rda')
# save(Mod_9_60_comb_int_a_2, file = 'Mod_9_60_comb_int_a_2.Rda')
# save(Mod_9_60_comb_hour_1, file = 'Mod_9_60_comb_hour_1')
# save(Mod_9_60_comb_hour_2, file = 'Mod_9_60_comb_hour_2')
# save(Mod_9_60_comb_week_1, file = 'Mod_9_60_comb_week_1')
# save(Mod_9_60_comb_week_2, file = 'Mod_9_60_comb_week_2')

```
,(?<=\,)(.*?)(?=\))

#Load model output
```{r, cache = TRUE}
path = "~/Desktop/Master2023/Data/Output_data/New_Best_NWP_model_output/"
load(paste0(path, "Mod_9_60_inter.Rda"))
load(paste0(path, "Mod_9_60_year_c.Rda"))
load(paste0(path, "Mod_9_60_year_f.Rda"))
load(paste0(path, "Mod_9_60_hour_c.Rda"))
load(paste0(path, "Mod_9_60_hour_f.Rda"))
load(paste0(path, "Mod_9_60_hour_sin.Rda"))
load(paste0(path, "Mod_9_60_week_c.Rda"))
load(paste0(path, "Mod_9_60_week_f.Rda"))
load(paste0(path, "Mod_9_60_week_sin.Rda"))
load(paste0(path, "Mod_9_60_week_sin_2.Rda"))
load(paste0(path, "Mod_9_60_week_sin_3.Rda"))
load(paste0(path, "Mod_9_60_month_c.Rda"))
load(paste0(path, "Mod_9_60_month_f.Rda"))
load(paste0(path, "Mod_9_60_month_sin.Rda"))
load(paste0(path, "Mod_9_60_season_c.Rda"))
load(paste0(path, "Mod_9_60_season_f.Rda"))
load(paste0(path, "Mod_9_60_season_sin.Rda"))
load(paste0(path, "Mod_9_60_NWP1.Rda"))
load(paste0(path, "Mod_9_60_NWP2.Rda"))
load(paste0(path, "Mod_9_60_climatology.Rda"))

load(paste0(path, "Mod_9_60_comb_a_0.Rda"))
load(paste0(path, "Mod_9_60_comb_a_1.Rda")) 
load(paste0(path, "Mod_9_60_comb_a_2.Rda"))

load(paste0(path, "Mod_9_60_int_a_0.Rda"))
load(paste0(path, "Mod_9_60_int_b_0.Rda"))
load(paste0(path, "Mod_9_60_int_c_0.Rda"))

load(paste0(path, "Mod_9_60_comb_int_c_0.Rda"))
load(paste0(path, "Mod_9_60_comb_int_c_1.Rda"))
load(paste0(path, "Mod_9_60_comb_int_c_2.Rda"))

load(paste0(path, "Mod_9_60_comb_int_b_0.Rda"))
load(paste0(path, "Mod_9_60_comb_int_b_1.Rda"))
load(paste0(path, "Mod_9_60_comb_int_b_2.Rda"))

load(paste0(path, "Mod_9_60_comb_int_a_0.Rda"))
load(paste0(path, "Mod_9_60_comb_int_a_1.Rda"))
load(paste0(path, "Mod_9_60_comb_int_a_2.Rda"))

load(paste0(path, "Mod_9_60_comb_hour_1.Rda"))
load(paste0(path, "Mod_9_60_comb_hour_2.Rda"))

load(paste0(path, "Mod_9_60_comb_week_1.Rda"))
load(paste0(path, "Mod_9_60_comb_week_2.Rda"))


load(paste0(path, "Mod_9_120_NWP2.Rda"))
load(paste0(path, "Mod_9_120_NWP1.Rda"))
load(paste0(path, "Mod_9_120_climatology.Rda"))

load(paste0(path, "Mod_9_120_NWP1_per32.Rda"))
load(paste0(path, "Mod_9_120_NWP1_per16.Rda"))
load(paste0(path, "Mod_9_120_NWP1_per8.Rda"))
load(paste0(path, "Mod_9_120_NWP1_per4.Rda"))
load(paste0(path, "Mod_9_120_NWP1_per2.Rda"))
load(paste0(path, "Mod_9_120_NWP1_per1.Rda"))
```

# 4) Quantile Regression Models with All lead Times
In this section we first look at: 
- 4a) Single time covariates 
- 4b) Climatology and NWP vars as single predictors.
- 4c) Full time covariates
- 4d) Interaction models
- 4e) NWP with Interaction (hour:week)
- 4f) NWP with Interaction (hour:month)
- 4g) NWP with Interaction (hour:season)
- 4h) NWP with just hour
- 4g) NWP with just week

## 4a) Single Time covariate models
```{r, eval = FALSE}
Mod_9_60_inter = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_year_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ year')
Mod_9_60_year_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(year)')

Mod_9_60_hour_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ hour')
Mod_9_60_hour_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(hour)')
Mod_9_60_hour_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * hour/4) + sin(2*pi * hour/4)')

Mod_9_60_week_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ week')
Mod_9_60_week_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(week)')
Mod_9_60_week_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/52) + sin(2*pi * week/52)')
Mod_9_60_week_sin_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/53) + sin(2*pi * week/53)')
Mod_9_60_week_sin_3 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/52.5) + sin(2*pi * week/52.5)')

Mod_9_60_month_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ month')
Mod_9_60_month_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(month)')
Mod_9_60_month_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * month/12) + sin(2*pi * month/12)')

Mod_9_60_season_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ season')
Mod_9_60_season_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(season)')
Mod_9_60_season_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * season/4) + sin(2*pi * season/4)')

```

## Plotting functions
```{r, cache = TRUE}
plot_func = function(function_list = c(),
                     legend_input= c('Climatology', '1 NWP pred', '2 NWP preds'),
                     title = '',
                     lead_time_interval = c(1,240),
                     climatology_ref = FALSE,
                     legend_place = 'top'){
    low = 1
    upp = 500
    ax = pretty(low:upp, 9)
    cols = c('black', 'brown1', 'dodgerblue1', 'orange', 'green')
    dat = get(function_list[1])
    if (climatology_ref==TRUE){
        plot_data = dat$Results[, .(mean_test_loss = mean(clima_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>=lead_time_interval[1] & lead_time <=lead_time_interval[2],mean(clima_loss)])
    } else{
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>=lead_time_interval[1] & lead_time <=lead_time_interval[2],mean(test_loss)])
    }
    matplot(low:upp, plot_data[low:upp,mean_test_loss] , type = 'l', ylim = c(0, 25), lty = 1,
            xaxt = 'n', xlab = 'Horizon (days)', ylab = 'Pinball loss', main = paste0(title,': 60 day window (Test)'), col = cols[1])
    legend(legend_place, lty = 1, cex=0.6, col = c('black', 'brown1', 'dodgerblue1', 'orange', 'green'),
           legend = legend_input)
    axis(1, at = ax, labels = ax/4)
    
    for (i in 2:length(function_list)){
        dat = get(function_list[i])
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>=lead_time_interval[1] & lead_time <=lead_time_interval[2],mean(test_loss)])
        matlines(low:upp, plot_data[low:upp,mean_test_loss], col = cols[i], lty = ifelse(i==2, 1, 2))
    }
}

plot_month = function(function_list = c(),
                     legend_input= c('Climatology', '1 NWP pred', '2 NWP preds'),
                     title = '',
                     climatology_ref = FALSE,
                     legend_place = 'top'){
    low = 1
    upp = 12
    ax = month.abb
    cols = c('black', 'brown1', 'dodgerblue1', 'orange', 'green')
    dat = get(function_list[1])
    if (climatology_ref==TRUE){
        plot_data = dat$Results[, .(mean_test_loss = mean(clima_loss)), keyby=.(horizon =month(date))]
    } else{
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =month(date))]
    }
    matplot(low:upp, plot_data[low:upp,mean_test_loss] , type = 'l', ylim = c(0, 25), lty = 1,
            xaxt = 'n', xlab = 'Month', ylab = 'Pinball loss', main = paste0(title,': 60 day window (Test)'), col = cols[1])
    legend(legend_place, lty = 1, cex=0.6, col = c('black', 'brown1', 'dodgerblue1', 'orange', 'green'),
           legend = legend_input)
    axis(1, at = 1:12, labels = ax)
    
    for (i in 2:length(function_list)){
        dat = get(function_list[i])
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =month(date))]
        matlines(low:upp, plot_data[low:upp,mean_test_loss], col = cols[i], lty = ifelse(i==2, 1, 2))
    }
}
```

## Plotting Time Covariates
```{r, cache=TRUE}
plot_func(c('Mod_9_60_inter', 'Mod_9_60_year_c', 'Mod_9_60_year_f'),
          title = 'Year', legend_input = c('Intercept', 'Year (cont)', 'Year (factor)'), legend_place = 'bottomright')
plot_func(c('Mod_9_60_hour_c', 'Mod_9_60_hour_f', 'Mod_9_60_hour_sin'), legend_place = 'bottomright',
          title = 'Hour', legend_input = c('Hour (cont)', 'Hour (factor)', 'Hour sinusoidal'))
plot_func(c('Mod_9_60_week_c', 'Mod_9_60_week_f', 'Mod_9_60_week_sin', 'Mod_9_60_week_sin_2','Mod_9_60_week_sin_3'), legend_place = 'bottomright',
          title = 'Week', legend_input = c('Week (cont)', 'Week (factor)', 'Week sinusoidal(52)','Week sinusoidal(53)','Week sinusoidal(52.5)'))
plot_func(c('Mod_9_60_month_c', 'Mod_9_60_month_f', 'Mod_9_60_month_sin'), legend_place = 'bottomright',
           title = 'Month', legend_input = c('Month (cont)', 'Month (factor)', 'Month sinusoidal'))
plot_func(c('Mod_9_60_season_c', 'Mod_9_60_season_f', 'Mod_9_60_season_sin'), legend_place = 'bottomright',
          title = 'Season', legend_input = c('Season (cont)', 'Season (factor)', 'Season sinusoidal'))
```

1) Continuous year is better 22.44 (Almost same as intercept) 
2) hour as factor better 22.1 (almost same as intercept)
3) Cont week is hopeless, as factor good, best is 52 weeks of  9.96
4) Month as factor is better 10.48
5) Season as factor 13.48

## 4b) Trying climatology and NWP vars
```{r, eval=FALSE}
Mod_9_60_NWP1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_NWP2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_climatology = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)
```
scp  eirikhsj@abacus-as.uio.no:~/Mod_9_125_NWP1_lead_time.Rda  /Users/Eirik/Desktop/Master2023/Output_data/New_Best_NWP_model_output

```{r, cahce = TRUE}
plot_func(c('Mod_9_60_climatology','Mod_9_60_NWP1', 'Mod_9_60_NWP2'), 
          title = 'Climatology + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240),
          legend_input= c('Climatology','NWP1','NWP2'))
plot_month(c('Mod_9_60_climatology','Mod_9_60_NWP1', 'Mod_9_60_NWP2'), 
           title = 'Climatology + NWP1 + NWP2', climatology_ref = TRUE,
          legend_input= c('Climatology','NWP1','NWP2')) 
```

1) climatology is very good, 
2) there seems to be pretty good skill at the beginning
3) we are doing better in winter than in summer. 
4) Virtually no skill using information from previous month NWP2. 
5) Can we improve model with the time covariates?

## 4c) FullTime covariate models
```{r, eval = FALSE}
Mod_9_60_comb_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_a_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg',window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_a_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'qreg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
```


as.factor(month) +  as.factor(season) leads to an undefined matrix, so we have to go with an alternative. 

```{r, cache = TRUE}
plot_func(c('Mod_9_60_comb_a_0','Mod_9_60_comb_a_1', 'Mod_9_60_comb_a_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE,legend_input= c('Time covariates', '+ 1 NWP', '+ 2 NWP'),lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_comb_a_0','Mod_9_60_comb_a_1', 'Mod_9_60_comb_a_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE,legend_input= c('Time covariates', '+ 1 NWP', '+ 2 NWP')) 
```
1) This is a better climatology than using the quantile directly. 9.04
2) Including the NWP2 very slightly increases the performance of the model. 8.11 vs 8.19 overall
3) This increase comes at the beginning, so it seems worth it, contributes the first 10 days, 

first 10 days is 5.78 vs 5.13
first 20 days is 6.27 vs 6.41
first 30 days is 7.45 vs 7.27

days 10-20 i 7.6550 vs 7.6658

We can again outperform the climatology model on a predictive task by using time covariates.

## 4d) Interaction models
```{r, eval = FALSE}
Mod_9_60_int_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(season)')
Mod_9_60_int_b_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month)')
Mod_9_60_int_c_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week)')
```

### Plot
```{r, cache = TRUE}
plot_func(c('Mod_9_60_int_a_0','Mod_9_60_int_b_0', 'Mod_9_60_int_c_0'), 
          title = 'Interactions hour with season, month week', climatology_ref = FALSE,
          legend_input= c('Hour:Season', 'Hour:Month', 'Hour:Week'))
plot_month(c('Mod_9_60_int_a_0','Mod_9_60_int_b_0', 'Mod_9_60_int_c_0'), 
          title = 'Interactions hour with season, month week', climatology_ref = FALSE,
          legend_input= c('Hour:Season', 'Hour:Month', 'Hour:Week')) 
```
1) Hour:Week is the best one, and a better model than climatology. 

## 4e) NWP with Interaction models (hour:week)
```{r, eval = FALSE}
Mod_9_60_comb_int_c_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
Mod_9_60_comb_int_c_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
Mod_9_60_comb_int_c_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'qreg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
```
1) Here we cannot run week and sin(week) together. 

```{r, cache=TRUE}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_c_0','Mod_9_60_comb_int_c_1', 'Mod_9_60_comb_int_c_2'), 
          title = 'Interaction hour:week + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_c_0','Mod_9_60_comb_int_c_1', 'Mod_9_60_comb_int_c_2'), 
          title = 'Interaction hour:week + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80
```
-Interactions worsens the NWP models

## 4f) NWP with Interaction models (hour:month)
```{r, eval = FALSE}
Mod_9_60_comb_int_b_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', 
                                      window = 60, cores = 48, 
                                      formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month) + cos(2*pi * week/52) + sin(2*pi * week/52) + year')
Mod_9_60_comb_int_b_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', 
                                      window = 60, cores = 48, 
                                      formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month) + cos(2*pi * week/52) + sin(2*pi * week/52) + year')
Mod_9_60_comb_int_b_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'qreg', 
                                      window = 60, cores = 48, 
                                      formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month) + cos(2*pi * week/52) + sin(2*pi * week/52) + year')
```

```{r, cahce = TRUE}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_b_0','Mod_9_60_comb_int_b_1', 'Mod_9_60_comb_int_b_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_b_0','Mod_9_60_comb_int_b_1', 'Mod_9_60_comb_int_b_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80
```

## 4g) NWP with Interaction models (hour:season)
```{r, eval = FALSE}
Mod_9_60_comb_int_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'qreg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year')

Mod_9_60_comb_int_a_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg',window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season)  + cos(2*pi * week/52) + 
                                    sin(2*pi * week/52) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_int_a_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'qreg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season)  + cos(2*pi * week/52) + 
                                    sin(2*pi * week/52) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
```

```{r, cache=TRUE}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_a_0','Mod_9_60_comb_int_a_1', 'Mod_9_60_comb_int_a_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_a_0','Mod_9_60_comb_int_a_1', 'Mod_9_60_comb_int_a_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80
```

So based on this is seems that the best model is the one with just the NWP, at least for the first 20 days. 
Might be interesting to check if we can add hour and week a simpler comb model basically. 

## 4h) NWP with Just hour
```{r, eval = FALSE}
Mod_9_60_comb_hour_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour)')

Mod_9_60_comb_hour_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'qreg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour)')

```


```{r, cache = TRUE}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_hour_1','Mod_9_60_comb_hour_2'), 
          title = 'Just hour + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_hour_1','Mod_9_60_comb_hour_2'), 
          title = 'Just hour + NWP1 + NWP2', climatology_ref = TRUE) 
```
## 4i) NWP with Just week
```{r, eval = FALSE}
Mod_9_60_comb_week_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(week)')

Mod_9_60_comb_week_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'qreg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(week)')
```

```{r}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_week_1','Mod_9_60_comb_week_2'), 
          title = 'Just week + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_week_1','Mod_9_60_comb_week_2'), 
          title = 'Just week + NWP1 + NWP2', climatology_ref = TRUE) 
```





# 5) Quantile Regression with daily training and prediction 
```{r}
Interval_Mod_9_125_NWP1_1day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 1*4)
Interval_Mod_9_125_NWP1_2day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 2*4)
Interval_Mod_9_125_NWP1_4day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 4*4)
Interval_Mod_9_125_NWP1_8day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 8*4)
Interval_Mod_9_125_NWP1_16day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 16*4)
Interval_Mod_9_125_NWP1_32day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 32*4)
Interval_Mod_9_125_NWP1_125day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 125*4)

save(Interval_Mod_9_125_NWP1_1day, file = "Interval_Mod_9_125_NWP1_1day.Rda")
save(Interval_Mod_9_125_NWP1_2day, file = "Interval_Mod_9_125_NWP1_2day.Rda")
save(Interval_Mod_9_125_NWP1_4day, file = "Interval_Mod_9_125_NWP1_4day.Rda")
save(Interval_Mod_9_125_NWP1_8day, file = "Interval_Mod_9_125_NWP1_8day.Rda")
save(Interval_Mod_9_125_NWP1_16day, file = "Interval_Mod_9_125_NWP1_16day.Rda")
save(Interval_Mod_9_125_NWP1_32day, file = "Interval_Mod_9_125_NWP1_32day.Rda")
save(Interval_Mod_9_125_NWP1_125day, file = "Interval_Mod_9_125_NWP1_125day.Rda")
```


scp eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_NWP1_1day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_NWP1_2day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_NWP1_4day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_NWP1_8day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_NWP1_16day.Rda  eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_NWP1_32day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_NWP1_125day.Rda /Users/Eirik/Desktop/Master2023/Output_data/New_Best_NWP_model_output
banjogitarharingfele99

```{r}
Interval_Mod_5_125_NWP1_1day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 1*4)
Interval_Mod_5_125_NWP1_2day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 2*4)
Interval_Mod_5_125_NWP1_4day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 4*4)
Interval_Mod_5_125_NWP1_8day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 8*4)
Interval_Mod_5_125_NWP1_16day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 16*4)
Interval_Mod_5_125_NWP1_32day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 32*4)
Interval_Mod_5_125_NWP1_125day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.5, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ -1', interval_k = 125*4)

save(Interval_Mod_5_125_NWP1_1day, file = "Interval_Mod_5_125_NWP1_1day.Rda")
save(Interval_Mod_5_125_NWP1_2day, file = "Interval_Mod_5_125_NWP1_2day.Rda")
save(Interval_Mod_5_125_NWP1_4day, file = "Interval_Mod_5_125_NWP1_4day.Rda")
save(Interval_Mod_5_125_NWP1_8day, file = "Interval_Mod_5_125_NWP1_8day.Rda")
save(Interval_Mod_5_125_NWP1_16day, file = "Interval_Mod_5_125_NWP1_16day.Rda")
save(Interval_Mod_5_125_NWP1_32day, file = "Interval_Mod_5_125_NWP1_32day.Rda")
save(Interval_Mod_5_125_NWP1_125day, file = "Interval_Mod_5_125_NWP1_125day.Rda")
```

divide by individual variance forcing NWP to have mean and variance equal to the climatology mean. 

For large quantiles might not be spread out enough. 

If done differently the coefficients should be more toward 0. 

Check the 0.5 to see if there is a over dispersion effect. 

```{r}
#pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/BetaNWPcomp1.pdf", height = 7, width = 7, pointsize = 12)

plot(Interval_Mod_9_125_NWP1_1day$Results[, mean(coef_NWP1_90), by = lead_time], type = 'l', ylab = expression("NWP " * beta *  " -coefficient"), main = expression(beta *  " -coefficient for NWP-models over different training periods"), xlab = "Lead time", col = 5)
lines(Interval_Mod_9_125_NWP1_2day$Results[, mean(coef_NWP1_90), by = lead_time], col = 8)
lines(Interval_Mod_9_125_NWP1_4day$Results[, mean(coef_NWP1_90), by = lead_time], col = 2)
lines(Interval_Mod_9_125_NWP1_8day$Results[, mean(coef_NWP1_90), by = lead_time], col = 3)
lines(Interval_Mod_9_125_NWP1_16day$Results[, mean(coef_NWP1_90), by = lead_time], col = 4)
lines(Interval_Mod_9_125_NWP1_32day$Results[, mean(coef_NWP1_90), by = lead_time], col = 6)
lines(Interval_Mod_9_125_NWP1_125day$Results[, mean(coef_NWP1_90), by = lead_time], col = 'red')

abline(h = 1)
legend("topleft", lty = 1, title = "Training Interval:", cex = 0.7, pch = 16, col = c(5,8, 2, 3, 4,6, 'red'), legend = c("1 day", "2 days", "4 days","8 days", "16 days", "32 days", "125 days"))
#dev.off()

```
## 0.5 quantle to check for climate change
```{r}
plot(Interval_Mod_5_125_NWP1_1day$Results[, mean(coef_NWP1_50), by = lead_time], type = 'l', ylab = expression("NWP " * beta *  " -coefficient"), main = expression(beta *  " -coefficient for NWP-models over different training periods"), xlab = "Lead time", col = 5)
lines(Interval_Mod_5_125_NWP1_2day$Results[, mean(coef_NWP1_50), by = lead_time], col = 8)
lines(Interval_Mod_5_125_NWP1_4day$Results[, mean(coef_NWP1_50), by = lead_time], col = 2)
lines(Interval_Mod_5_125_NWP1_8day$Results[, mean(coef_NWP1_50), by = lead_time], col = 3)
lines(Interval_Mod_5_125_NWP1_16day$Results[, mean(coef_NWP1_50), by = lead_time], col = 4)
lines(Interval_Mod_5_125_NWP1_32day$Results[, mean(coef_NWP1_50), by = lead_time], col = 6)
lines(Interval_Mod_5_125_NWP1_125day$Results[, mean(coef_NWP1_50), by = lead_time], col = 'red')

abline(h = 1)
legend("bottomright", lty = 1, title = "Training Interval:", cex = 0.7, pch = 16, col = c(5,8, 2, 3, 4,6, 'red'), legend = c("1 day", "2 days", "4 days","8 days", "16 days", "32 days", "125 days"))
```
## Month models (NOT IMPORTANT)
```{r}
Interval_Mod_9_125_NWP1_m_1day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', interval_k = 1*4)
Interval_Mod_9_125_NWP1_m_2day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', interval_k = 2*4)

Interval_Mod_9_125_NWP1_m_4day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', interval_k = 4*4)

Interval_Mod_9_125_NWP1_m_8day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', interval_k = 8*4)

Interval_Mod_9_125_NWP1_m_16day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', interval_k = 16*4)

Interval_Mod_9_125_NWP1_m_32day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', interval_k = 32*4)
Interval_Mod_9_125_NWP1_m_125day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, formula  = 'PC1 ~ 1', interval_k = 125*4)

save(Interval_Mod_9_125_NWP1_m_1day, file = "Interval_Mod_9_125_NWP1_m_1day.Rda")
save(Interval_Mod_9_125_NWP1_m_2day, file = "Interval_Mod_9_125_NWP1_m_2day.Rda")
save(Interval_Mod_9_125_NWP1_m_4day, file = "Interval_Mod_9_125_NWP1_m_4day.Rda")
save(Interval_Mod_9_125_NWP1_m_8day, file = "Interval_Mod_9_125_NWP1_m_8day.Rda")
save(Interval_Mod_9_125_NWP1_m_16day, file = "Interval_Mod_9_125_NWP1_m_16day.Rda")
save(Interval_Mod_9_125_NWP1_m_32day, file = "Interval_Mod_9_125_NWP1_m_32day.Rda")
```


```{r}
plot(Interval_Mod_9_125_NWP1_m_1day$Results[, mean(coef_NWP1_90), by = lead_time], type = 'l', ylab = expression("NWP " * beta *  " -coefficient"), main = expression(beta *  " -coefficient for NWP-models over different training periods"), xlab = "Lead time", col = 5)
lines(Interval_Mod_9_125_NWP1_m_2day$Results[, mean(coef_NWP1_90), by = lead_time], col = 8)
lines(Interval_Mod_9_125_NWP1_m_4day$Results[, mean(coef_NWP1_90), by = lead_time], col = 2)
lines(Interval_Mod_9_125_NWP1_m_8day$Results[, mean(coef_NWP1_90), by = lead_time], col = 3)
lines(Interval_Mod_9_125_NWP1_m_16day$Results[, mean(coef_NWP1_90), by = lead_time], col = 4)
lines(Interval_Mod_9_125_NWP1_m_32day$Results[, mean(coef_NWP1_90), by = lead_time], col = 6)
lines(Interval_Mod_9_125_NWP1_m_125day$Results[, mean(coef_NWP1_90), by = lead_time], col = 'red')
abline(h = 1)
legend("topleft", lty = 1, title = "Training Interval:", cex = 0.7, pch = 16, col = c(5,8, 2, 3, 4,6, 'red'), legend = c("1 day", "2 days", "4 days","8 days", "16 days", "32 days", "125 days"))
```


```{r}
Interval_Mod_9_125_comb_int_a_1_1day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year', interval_k = 1*4)
Interval_Mod_9_125_comb_int_a_1_2day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year', interval_k = 2*4)
Interval_Mod_9_125_comb_int_a_1_4day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year', interval_k = 4*4)
Interval_Mod_9_125_comb_int_a_1_8day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year', interval_k = 8*4)
Interval_Mod_9_125_comb_int_a_1_16day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year', interval_k = 16*4)
Interval_Mod_9_125_comb_int_a_1_32day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year', interval_k = 32*4)
Interval_Mod_9_125_comb_int_a_1_125day = rolling_mod_NWP_interval('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'qreg', window = 125, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year', interval_k = 125*4)

save(Interval_Mod_9_125_comb_int_a_1_1day, file = "Interval_Mod_9_125_comb_int_a_1_1day.Rda")
save(Interval_Mod_9_125_comb_int_a_1_2day, file = "Interval_Mod_9_125_comb_int_a_1_2day.Rda")
save(Interval_Mod_9_125_comb_int_a_1_4day, file = "Interval_Mod_9_125_comb_int_a_1_4day.Rda")
save(Interval_Mod_9_125_comb_int_a_1_8day, file = "Interval_Mod_9_125_comb_int_a_1_8day.Rda")
save(Interval_Mod_9_125_comb_int_a_1_16day, file = "Interval_Mod_9_125_comb_int_a_1_16day.Rda")
save(Interval_Mod_9_125_comb_int_a_1_32day, file = "Interval_Mod_9_125_comb_int_a_1_32day.Rda")
save(Interval_Mod_9_125_comb_int_a_1_125day, file = "Interval_Mod_9_125_comb_int_a_1_125day.Rda")
```

```{r}
pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/BetaNWPcomp2.pdf", height = 7, width = 7, pointsize = 12)

plot(Interval_Mod_9_125_comb_int_a_1_1day$Results[, mean(coef_NWP1_90), by = lead_time], type = 'l', ylab = expression("NWP " * beta *  " -coefficient"), main = expression(beta *  " -coefficient for NWP-models over different training periods"), xlab = "Lead time", col = 5)
lines(Interval_Mod_9_125_comb_int_a_1_2day$Results[, mean(coef_NWP1_90), by = lead_time], col = 8)
lines(Interval_Mod_9_125_comb_int_a_1_4day$Results[, mean(coef_NWP1_90), by = lead_time], col = 2)
lines(Interval_Mod_9_125_comb_int_a_1_8day$Results[, mean(coef_NWP1_90), by = lead_time], col = 3)
lines(Interval_Mod_9_125_comb_int_a_1_16day$Results[, mean(coef_NWP1_90), by = lead_time], col = 4)
lines(Interval_Mod_9_125_comb_int_a_1_32day$Results[, mean(coef_NWP1_90), by = lead_time], col = 6)
lines(Interval_Mod_9_125_comb_int_a_1_125day$Results[, mean(coef_NWP1_90), by = lead_time], col = 'red')
abline(h = 1, col = 'grey', lty = 2)
abline(h = 0, col = 1)
legend("bottomleft", lty = 1, title = "Training Interval:", cex = 0.7, pch = 16, col = c(5,8, 2, 3, 4,6, 'red'), legend = c("1 day", "2 days", "4 days","8 days", "16 days", "32 days", "125 days"))
dev.off()
```

```{r}
plot_func(c('Mod_9_60_climatology','Interval_Mod_9_125_NWP1_1day','Interval_Mod_9_125_NWP1_2day','Interval_Mod_9_125_NWP1_2day','Interval_Mod_9_125_NWP1_4day','Interval_Mod_9_125_NWP1_8day','Interval_Mod_9_125_NWP1_8day','Interval_Mod_9_125_NWP1_8day'), 
          title = 'NWP1 models for different training', climatology_ref = TRUE,lead_time_interval = c(1,500))
plot_month(c('Mod_9_60_climatology', 'Interval_Mod_9_125_NWP1_1day','Interval_Mod_9_125_NWP1_2day'), 
          title = 'Just week + NWP1', climatology_ref = TRUE) 
```

# 6) Considering different scoring intervals 

## 6a) Static intervals
```{r, cache = TRUE}
for (i in c(0.5,1,2,4,8,16,32)){
    Mod_9_120_NWP1_check_climat$Results[, paste0('group',i):= (lead_time-1)%/%(4*i)]
    Mod_9_120_NWP1_check_climat$Results[, c(paste0("PC_", i, "days"), 
                                      paste0("clima_pred", i, "days")):= .(mean(PC1),  mean(clima_pred)), by = .(get(paste0('group',i)), init_date)]
    Mod_9_120_NWP1_check_climat$Results[, paste0("loss_clima", i, "days") := pinball_loss(0.9,get(paste0("clima_pred", i, "days")),get(paste0("PC_", i, "days")))]
    Mod_9_120_NWP1_check_climat$Results[, paste0("pred", i, "days"):= .(mean(pred)), by = .(get(paste0('group',i)), init_date)]

    Mod_9_120_NWP1_check_climat$Results[, paste0("loss", i, "days") := pinball_loss(0.9,get(paste0("pred", i, "days")),get(paste0("PC_", i, "days")))]
}

Mod_9_120_NWP1_check_climat$Results[, clima_loss := pinball_loss(0.9, clima_pred,PC1)]
plot(Mod_9_120_NWP1_check_climat$Results[, mean(loss0.5days), by = group1], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_NWP1_check_climat$Results[, mean(loss_clima0.5days), by = group1], col = 'red')

plot(Mod_9_120_NWP1_check_climat$Results[, mean(loss1days), by = group1], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_NWP1_check_climat$Results[, mean(loss_clima1days), by = group1], col = 'red')

plot(Mod_9_120_NWP1_check_climat$Results[, mean(loss2days), by = group2], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_NWP1_check_climat$Results[, mean(loss_clima2days), by = group2], col = 'red')

plot(Mod_9_120_NWP1_check_climat$Results[, mean(loss4days), by = group4], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_NWP1_check_climat$Results[, mean(loss_clima4days), by = group4], col = 'red')

plot(Mod_9_120_NWP1_check_climat$Results[, mean(loss8days), by = group8], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_NWP1_check_climat$Results[, mean(loss_clima8days), by = group8], col = 'red')

plot(Mod_9_120_NWP1_check_climat$Results[, mean(loss16days), by = group16], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_NWP1_check_climat$Results[, mean(loss_clima16days), by = group16], col = 'red')

plot(Mod_9_120_NWP1_check_climat$Results[, mean(loss32days), by = group32], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_NWP1_check_climat$Results[, mean(loss_clima32days), by = group32], col = 'red')
```


```{r, cache = TRUE}
plot(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(test_loss), by = lead_time][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(pinball_loss(0.9,clima_pred,PC1)), by = lead_time][,V1]),xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(-0.1, 0.6), main = "Skill by Period", xlab = "Lead Time (Days)", ylab = "Skill Score")
abline(h = 0)
# lines(rep(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss1days), by = group1][,V1]/
#               Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima1days), by = group1][,V1]), each = 4),col = 'grey')
# 
# lines(rep(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss2days), by = group2][,V1]/
#                Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima2days), by = group2][,V1]), each = 8), col = 'grey')
lines(rep(1-  (Mod_9_120_NWP1_check_climat$Results[,mean(loss4days), by = group4][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima4days), by = group4][,V1]), each = 16), col = 'pink')
lines(rep(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss8days), by = group8][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima8days), by = group8][,V1]), each = 32),col = 'red')
lines(rep(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss16days), by = group16][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima16days), by = group16][,V1]),each = 64),col = 'blue')
lines(rep(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss32days), by = group32][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima32days), by = group32][,V1]),each = 128),col = 'orange')
legend("topright", lty = 1, title = "Scoring Interval:", cex = 0.7, pch = 16, col = c('black','grey', 'red', 'blue', 'orange'), legend = c("6-hour", "4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
```


## 6b) Skill Interval Rolling mean version
```{r, cache = TRUE}
for (i in c(0.5,1,2,4,8,16,32)){
    Mod_9_120_NWP1_check_climat$Results[, c(paste0("PC_", i, "days_roll"), 
                                      paste0("clima_pred", i, "days_roll")):= 
                                      .(rollapply(PC1, width = i*4, partial = TRUE, FUN = mean),
                                        rollapply(clima_pred, width = i*4, partial = TRUE, FUN = mean)), 
                                  by = .(init_date)]
    Mod_9_120_NWP1_check_climat$Results[, paste0("loss_clima", i, "days_roll") := pinball_loss(0.9,get(paste0("clima_pred", i, "days_roll")),get(paste0("PC_", i, "days_roll")))]
    Mod_9_120_NWP1_check_climat$Results[, c(paste0("pred", i, "days_roll")):= 
                               .(rollapply(pred, width = i*4, partial = TRUE, FUN = mean)), 
                           by = .(init_date)]
    Mod_9_120_NWP1_check_climat$Results[, paste0("loss", i, "days_roll") := pinball_loss(0.9,get(paste0("pred", i, "days_roll")),get(paste0("PC_", i, "days_roll")))]
}
```

### Plot output for Scoring_interval.pdf
```{r, cache = TRUE}
pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/Scoring_interval.pdf", height = 9, width = 9, pointsize = 12)
layout(matrix(c(1,2,3,3), 4, 1, byrow = TRUE))
par(mar = c(1, 3.4, 3, 3))

 ######## Climatology #############
plot(Mod_9_120_NWP1_check_climat$Results[,mean(pinball_loss(0.9,clima_pred,PC1)), by = lead_time][,V1],xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(2.7,11.2), main = "Scoring Intervals for Pinball Loss (Climatology) by Lead Time", xlab = "", ylab = "")
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima0.5days_roll), by = lead_time][,V1],col = 'grey')
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima1days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima2days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima4days_roll), by = lead_time][,V1],col = 'pink')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima8days_roll), by = lead_time][,V1],col = 'orange')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima16days_roll), by = lead_time][,V1],col = 'blue')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima32days_roll), by = lead_time][,V1],col = 'red')
mtext("Pinball Loss", side = 2, line = 3, cex = 0.8, padj = 1.2)
abline(v = 24*4 +2, lty = 3)
# legend("bottomright", lty = 1, title = "Scoring Interval:", cex = 0.7, pch = 16, col = c('black','grey','pink', 'red', 'blue', 'orange'), legend = c("6 hours", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
par(mar = c(1, 3.4, 3, 3))
############ NWP1 ##################
plot(Mod_9_120_NWP1_check_climat$Results[,mean(test_loss), by = lead_time][,V1],xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(2.7,11.2), main = "Scoring Intervals for Pinball Loss (NWP1) by Lead Time", xlab = "", ylab = "")
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss0.5days_roll), by = lead_time][,V1],col = 'grey')
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss1days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss2days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss4days_roll), by = lead_time][,V1],col = 'pink')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss8days_roll), by = lead_time][,V1],col = 'orange')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss16days_roll), by = lead_time][,V1],col = 'blue')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss32days_roll), by = lead_time][,V1],col = 'red')
mtext("Pinball Loss", side = 2, line = 3, cex = 0.8, padj = 1.2)
# legend("bottomright", lty = 1, title = "Scoring Interval:", cex = 0.7, pch = 16, col = c('black','grey','pink', 'red', 'blue', 'orange'), legend = c("6 hours", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
abline(v = 24*4 +2, lty = 3)

par(mar = c(5, 3.4, 3, 3))
###### SKILL ############
plot(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(test_loss), by = lead_time][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(pinball_loss(0.9,clima_pred,PC1)), by = lead_time][,V1]),xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty =1, ylim = c(-0.09, 0.7), main = "Scoring Intervals for Skill of NWP1 relative to Climatology by Lead Time", xlab = "", ylab = "")
abline(h = 0)
# lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss0.5days_roll), by = lead_time][,V1]/
#               Mod_9_120_NWP1_check_climat$Results[,mean(loss0.5days_roll), by = lead_time][,V1]),col = 'grey')
# lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss1days_roll), by = lead_time][,V1]/
#               Mod_9_120_NWP1_check_climat$Results[,mean(loss1days_roll), by = lead_time][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss2days_roll), by = lead_time][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima2days_roll), by = lead_time][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss4days_roll), by = lead_time][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima4days_roll), by = lead_time][,V1]),col = 'pink')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss8days_roll), by = lead_time][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima8days_roll), by = lead_time][,V1]),col = 'orange')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss16days_roll), by = lead_time][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima16days_roll), by = lead_time][,V1]),col = 'blue')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss32days_roll), by = lead_time][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima32days_roll), by = lead_time][,V1]),col = 'red')

legend("topright", lty = 1, title = "Scoring Interval:", cex = 1.1, pch = 16, col = c('black','grey','pink','orange', 'blue', 'red'), legend = c("6 hours", "2 days","4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
mtext("Skill Score", side = 2, line = 3, cex = 0.8, padj = 1.2)
mtext("Lead Time (Days)", side = 1, line = 3, cex = 0.8, padj = -1.)
abline(v = 24*4, lty = 3)
dev.off()
```

### Plot output for Scoring_interval_by_month.pdf
```{r}
pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/Scoring_interval_by_month.pdf", height = 9, width = 9, pointsize = 12)
layout(matrix(c(1,2,3,3), 4, 1, byrow = TRUE))
par(mar = c(1, 3.4, 3, 3))

 ######## Climatology #############
plot(Mod_9_120_NWP1_check_climat$Results[,mean(pinball_loss(0.9,clima_pred,PC1)), by = month][,V1],xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(0,15), main = "Scoring Intervals for Pinball Loss (Climatology) by Month", xlab = "", ylab = "")
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima0.5days_roll), by = month][,V1],col = 'grey')
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima1days_roll), by = month][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima2days_roll), by = month][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima4days_roll), by = month][,V1],col = 'pink')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima8days_roll), by = month][,V1],col = 'orange')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima16days_roll), by = month][,V1],col = 'blue')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima32days_roll), by = month][,V1],col = 'red')
mtext("Pinball Loss", side = 2, line = 3, cex = 0.8, padj = 1.2)
abline(v = 24*4 +2, lty = 3)
# legend("bottomright", lty = 1, title = "Scoring Interval:", cex = 0.7, pch = 16, col = c('black','grey','pink', 'red', 'blue', 'orange'), legend = c("6 hours", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(1, at = 1:12, labels = month.abb)
par(mar = c(1, 3.4, 3, 3))
############ NWP1 ##################
plot(Mod_9_120_NWP1_check_climat$Results[,mean(test_loss), by = month][,V1],xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(0,15), main = "Scoring Intervals for Pinball Loss (NWP1) by Month", xlab = "", ylab = "")
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss0.5days_roll), by = month][,V1],col = 'grey')
# lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss1days_roll), by = month][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss2days_roll), by = month][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss4days_roll), by = month][,V1],col = 'pink')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss8days_roll), by = month][,V1],col = 'orange')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss16days_roll), by = month][,V1],col = 'blue')
lines(Mod_9_120_NWP1_check_climat$Results[,mean(loss32days_roll), by = month][,V1],col = 'red')
mtext("Pinball Loss", side = 2, line = 3, cex = 0.8, padj = 1.2)
# legend("bottomright", lty = 1, title = "Scoring Interval:", cex = 0.7, pch = 16, col = c('black','grey','pink', 'red', 'blue', 'orange'), legend = c("6 hours", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(1, at = 1:12, labels = month.abb)
abline(v = 24*4 +2, lty = 3)

par(mar = c(5, 3.4, 3, 3))
###### SKILL ############
plot(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(test_loss), by = month][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(pinball_loss(0.9,clima_pred,PC1)), by = month][,V1]),xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty =1, ylim = c(-0.05, 0.25), main = "Scoring Intervals for Skill of NWP1 relative to Climatology by Month", xlab = "", ylab = "")
abline(h = 0)
# lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss0.5days_roll), by = month][,V1]/
#               Mod_9_120_NWP1_check_climat$Results[,mean(loss0.5days_roll), by = month][,V1]),col = 'grey')
# lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss1days_roll), by = month][,V1]/
#               Mod_9_120_NWP1_check_climat$Results[,mean(loss1days_roll), by = month][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss2days_roll), by = month][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima2days_roll), by = month][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss4days_roll), by = month][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima4days_roll), by = month][,V1]),col = 'pink')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss8days_roll), by = month][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima8days_roll), by = month][,V1]),col = 'orange')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss16days_roll), by = month][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima16days_roll), by = month][,V1]),col = 'blue')
lines(1 - (Mod_9_120_NWP1_check_climat$Results[,mean(loss32days_roll), by = month][,V1]/
              Mod_9_120_NWP1_check_climat$Results[,mean(loss_clima32days_roll), by = month][,V1]),col = 'red')

legend("topright", lty = 1, title = "Scoring Interval:", cex = 1.1, pch = 16, col = c('black','grey','pink','orange', 'blue', 'red'), legend = c("6 hours", "2 days","4 days","8 days", "16 days", "32 days"))
axis(1, at = 1:12, labels = month.abb)
mtext("Skill Score", side = 2, line = 3, cex = 0.8, padj = 1.2)
mtext("Month", side = 1, line = 3, cex = 0.8, padj = -1.)
abline(v = 24*4, lty = 3)
dev.off()
```

### Plot function
```{r}
Scoring_interval_plot = function(data = Mod_9_120_NWP1_check_climat$Results, by_var = 'month', lead_time_less_than = 240, intervals = c(0.5, 1,2,4,8,16,32), monthofinterest = c(1:12)){
    
    layout(matrix(c(1,2,3,3), 4, 1, byrow = TRUE))
    par(mar = c(1, 3.4, 3, 3))
    mx1 = max(data[month %in% monthofinterest & lead_time<=lead_time_less_than,mean(pinball_loss(0.9,clima_pred,PC1)), by = by_var][,V1])
        
     ######## Climatology #############
    plot(data[month %in% monthofinterest & lead_time<=lead_time_less_than,mean(pinball_loss(0.9,clima_pred,PC1)), by = by_var][,V1],xaxt = 'n',
                  type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(0,mx1+0.4), 
         main = "Scoring Intervals for Pinball Loss (Climatology) by Month", xlab = "", ylab = "")
    
    colz = c('grey','grey','grey','pink','orange','blue','red')
    for (i in intervals){
        lines(data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(get(paste0('loss_clima',i,'days_roll'))), by = by_var][,V1],col = colz[log(i*2, base =2)+1])
    }                  
    mtext("Pinball Loss", side = 2, line = 3, cex = 0.8, padj = 1.2)
    abline(v = 24*4 +2, lty = 3)
    if (by_var == 'month'){ axis(1, at = 1:12, labels = month.abb)
    } else{ axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))}

    par(mar = c(1, 3.4, 3, 3))
    
    ############ NWP1 ##################
    plot(data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(test_loss), by = by_var][,V1],xaxt = 'n',
                  type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(0,mx1+0.4),
         main = "Scoring Intervals for Pinball Loss (NWP1) by Month", xlab = "", ylab = "")

    for (i in intervals){
        lines(data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(get(paste0('loss',i,'days_roll'))), by = by_var][,V1],col = colz[log(i*2, base =2)+1])
    }     
    mtext("Pinball Loss", side = 2, line = 3, cex = 0.8, padj = 1.2)
    # legend("bottomright", lty = 1, title = "Scoring Interval:", cex = 0.7, pch = 16, col = c('black','grey','pink', 'red', 'blue', 'orange'), legend = c("6 hours", "2 days", "4 days","8 days", "16 days", "32 days"))
    if (by_var == 'month'){ axis(1, at = 1:12, labels = month.abb)
    } else{ axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))}
    abline(v = 24*4 +2, lty = 3)
    
    par(mar = c(5, 3.4, 3, 3))
    ###### SKILL ############
    mx = max(1 - (data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(test_loss), by = by_var][,V1]/
                  data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(pinball_loss(0.9,clima_pred,PC1)), by = by_var][,V1]))
    plot(1 - (data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(test_loss), by = by_var][,V1]/
                  data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(pinball_loss(0.9,clima_pred,PC1)), by = by_var][,V1]),xaxt = 'n',
                  type = 'l',col = rgb(0,0,0,1), lty =1, ylim = c(-0.05, mx+0.03), 
         main = "Scoring Intervals for Skill of NWP1 relative to Climatology by Month", xlab = "", ylab = "")
    abline(h = 0)
    for (i in intervals){
        lines(1 -(data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(get(paste0('loss',i,'days_roll'))), by = by_var][,V1]/
                  data[month %in% monthofinterest &lead_time<=lead_time_less_than,mean(get(paste0('loss_clima',i,'days_roll'))), by = by_var][,V1]),
        col = colz[log(i*2, base =2)+1])
    }  
    
    
    if (by_var == 'month'){ 
        axis(1, at = 1:12, labels = month.abb)
        mtext("Month", side = 1, line = 3, cex = 0.8, padj = -1.)
        legend("bottomright", lty = 1, title = "Scoring Interval:", cex = 1.1, pch = 16, col = c('black','grey','pink','orange', 'blue', 'red'), legend = c("6 hours", "2 days","4 days","8 days", "16 days", "32 days"))
    
    } else{ 
        axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
        mtext("Lead Time (Days)", side = 1, line = 3, cex = 0.8, padj = -1.)
        legend("topright", lty = 1, title = "Scoring Interval:", cex = 1.1, pch = 16, col = c('black','grey','pink','orange', 'blue', 'red'), legend = c("6 hours", "2 days","4 days","8 days", "16 days", "32 days"))
    
}
    mtext("Skill Score", side = 2, line = 3, cex = 0.8, padj = 1.2)
    abline(v = 24*4, lty = 3)
}

pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/Scoring_interval_by month_lead_less60.pdf", height = 9, width = 9, pointsize = 12)
    Scoring_interval_plot()
    dev.off()
```

### Attempt to plot vertical distribution
```{r}
unq = unique(Mod_9_120_NWP1_check_climat$Results[lead_time %in% c(186),init_date], col = 'red')
plot(Mod_9_120_NWP1_check_climat$Results[, mean(test_loss), keyby = lead_time], col = 'red',
     ylim = c(0,50))
for (i in 1:length(unq)){
points(Mod_9_120_NWP1_check_climat$Results[init_date ==unq[i] &lead_time %in% c(180:185), quantile(test_loss), keyby = lead_time], col = i)
}

plot(Mod_9_120_NWP1_check_climat$Results[lead_time<240, mean(test_loss), keyby = lead_time], col = 'red',type = 'l',
     ylim = c(0,50))
points(Mod_9_120_NWP1_check_climat$Results[lead_time %in% c(1,100,160, 185), quantile(test_loss), keyby = lead_time], cex = 0.7, pch = 16)
```


### Plotting of outliers
```{r}
# Mod_9_60_NWP1_check = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP_keep, 1, model = 'qreg', 
#                                 window = 120, cores = 48, formula  = 'PC1 ~ 1')

plot(Mod_9_120_NWP1_check$Results[!init_date%in% unique(Mod_9_120_NWP1_check$Results[test_loss >90, c(init_date)]), .(test_loss), by =lead_time], cex = 0.15, pch = 16, ylim = c(0,160), col = rgb(0,0,0,1))
colz = c(2:7)
for (i in c(1:26)){
    
    points(Mod_9_120_NWP1_check$Results[init_date%in% unique(Mod_9_120_NWP1_check$Results[test_loss >80, c(init_date)])[i] & test_loss>25, .(test_loss), by =lead_time], cex = 0.35, pch = 16, col = colz[i%%6 +1])
}

plot(Mod_9_120_NWP1_check_97_23$Results[!init_date%in% unique(Mod_9_120_NWP1_check_97_23$Results[pinball_loss(0.9,clima_pred,PC1) >80, c(init_date)]), .(pinball_loss(0.9,clima_pred,PC1)), by =lead_time], cex = 0.3, pch = 16, ylim = c(0,160), col = rgb(0,0,0,1))
for (i in c(1:8, 9:20)){
    points(Mod_9_120_NWP1_check_97_23$Results[init_date%in% unique(Mod_9_120_NWP1_check_97_23$Results[pinball_loss(0.9,clima_pred,PC1) >80, c(init_date)])[i] & test_loss>40, .(pinball_loss(0.9,clima_pred,PC1)), by =lead_time], cex = 0.5, pch = 16, col = colz[i%%6 +1])
}
```



```{r}
 ######## Climatology #############
II = Mod_9_120_NWP1_check_climat$Results[pinball_loss(0.9,clima_pred,PC1)<40,.I]


plot(Mod_9_120_NWP1_check_climat$Results[II,mean(pinball_loss(0.9,clima_pred,PC1)), by = lead_time][,V1],xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 1, ylim = c(2.7,11.2), main = "Scoring Intervals for Pinball Loss (Climatology) by Lead Time", xlab = "", ylab = "")
# lines(Mod_9_120_NWP1_check_climat$Results[II,mean(loss_clima0.5days_roll), by = lead_time][,V1],col = 'grey')
# lines(Mod_9_120_NWP1_check_climat$Results[II,mean(loss_clima1days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[II,mean(loss_clima2days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1_check_climat$Results[II,mean(loss_clima4days_roll), by = lead_time][,V1],col = 'pink')
lines(Mod_9_120_NWP1_check_climat$Results[II,mean(loss_clima8days_roll), by = lead_time][,V1],col = 'orange')
lines(Mod_9_120_NWP1_check_climat$Results[II,mean(loss_clima16days_roll), by = lead_time][,V1],col = 'blue')
lines(Mod_9_120_NWP1_check_climat$Results[II,mean(loss_clima32days_roll), by = lead_time][,V1],col = 'red')
mtext("Pinball Loss", side = 2, line = 3, cex = 0.8, padj = 1.2)
abline(v = 24*4 +2, lty = 3)
# legend("bottomright", lty = 1, title = "Scoring Interval:", cex = 0.7, pch = 16, col = c('black','grey','pink', 'red', 'blue', 'orange'), legend = c("6 hours", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
```
### Checking Effect of median/mean
```{r}
plot(Mod_9_120_NWP1_check_climat$Results[,median(pinball_loss(0.9,clima_pred,PC1)), by = lead_time][,V1],xaxt = 'n',
     type = 'l',col = 'black', lty = 1, ylim = c(1.95,11), main = "Pinball Loss Effect of median/mean", xlab = "", ylab = "")
lines(Mod_9_120_NWP1_check_climat$Results[,mean(pinball_loss(0.9,clima_pred,PC1)), by = lead_time][,V1],xaxt = 'n',
      type = 'l',col = 'black', lty = 2)
lines(Mod_9_120_NWP1_check_climat$Results[,mean(test_loss), by = lead_time][,V1],xaxt = 'n',
     type = 'l',col = 'red', lty = 2)
lines(Mod_9_120_NWP1_check_climat$Results[,median(test_loss), by = lead_time][,V1],xaxt = 'n',
     type = 'l',col = 'red')
legend('bottomright', legend = c('Median Climatology', 'Median NWP1','Mean Climatology', 'Mean NWP1'), pch = 16,lty = c(1,1,2,2), col = c('black', 'red', 'black', 'red'))
```

### Fancy plot of monthly ERA distribution
```{r}
#library("patchwork")
PC_Plotting = ERA$dt_test
PC_Plotting[,Month := unique(lincoln_weather$Month)[month(date)]]

pdf("/Users/Eirik/Desktop/Master2023/ExportedPlots/Factor_loadings_by_month.pdf", height = 7, width = 9, pointsize = 12)

plot1 = ggplot(
     PC_Plotting[], 
     aes(x = `PC1`, y = `Month`, fill = stat(x))
 ) +
     geom_density_ridges_gradient(scale = 3, size = 0.3, rel_min_height = 0.01) +
     scale_fill_viridis_c(name = "Temp. [F]", option = "C") +
     theme(legend.position="none")+
     labs(title = '', x = "First Factor Loading")

plot2 =  ggplot(
     PC_Plotting[], 
     aes(x = `PC2`, y = `Month`, fill = stat(x))
 ) +
     geom_density_ridges_gradient(scale = 3, size = 0.3, rel_min_height = 0.01) +
     scale_fill_viridis_c(name = "Temp. [F]", option = "C") +
    theme(legend.position="none")+
     labs(title = '', y ="", x = "Second Factor Loading") +
    theme(axis.title.y = element_blank(), axis.text.y = element_blank(),axis.ticks.length = unit(0, "mm")) +
    xlim(-400,400) 
    
ggp_all <- (plot1 + plot2) +    # Create grid of plots with title
  plot_annotation(title = "First and Second Factor Loading of ERA temperature") & 
  theme(plot.title = element_text(hjust = 0.5))
ggp_all
dev.off()
```


# Code for saving and relocating files

save(Mod_9_60_comb_int_a_0, file = 'Mod_9_60_comb_int_a_0.Rda')
save(Mod_9_60_comb_int_a_1, file = 'Mod_9_60_comb_int_a_1.Rda')
save(Mod_9_60_comb_int_a_2, file = 'Mod_9_60_comb_int_a_2.Rda')

scp eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_comb_int_a_1_1day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_comb_int_a_1_2day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_comb_int_a_1_4day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_comb_int_a_1_8day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_comb_int_a_1_16day.Rda eirikhsj@abacus-as.uio.no:~/Interval_Mod_9_125_comb_int_a_1_32day.Rda /Users/Eirik/Desktop/Master2023/Output_data/New_Best_NWP_model_output


eirikhsj@abacus-as.uio.no:~/Factor10_inter1_6.Rda 
eirikhsj@abacus-as.uio.no:~/Factor10_inter1_9.Rda
eirikhsj@abacus-as.uio.no:~/Factor10_inter1_10.Rda

eirikhsj@abacus-as.uio.no:/mn/kadingir/datascience_000000/eirikhsj
