---
title: "Best NWP FINAL"
author: "Eirik Sjåvik"
date: "2023-03-06"
output: html_document
---


```{r}
library(DemandForecast)
library(data.table)
library(ncdf4)
library(parallel)
library(mgcv)
library(quantreg)

ERA_NWP = get_ERA_NWP(ERA_path = "/mn/kadingir/datascience_000000/eirikhsj/PC_ERA_79_92.Rda", 
                      NWP_path ="/mn/kadingir/datascience_000000/eirikhsj/NWP_quant_1993_2023.Rda",
                      quant = "90", reweight = FALSE)

ERA_NWP[, season:= ifelse(month(date) %in% c(12,1,2), 1, 
                            ifelse(month(date) %in% c(3,4,5), 2,
                            ifelse(month(date) %in% c(6,7,8), 3, 4)))]
```

```{r}
save(Mod_9_60_inter, file = 'Mod_9_60_inter.Rda')
save(Mod_9_60_year_c, file = 'Mod_9_60_year_c.Rda')
save(Mod_9_60_year_f, file = 'Mod_9_60_year_f.Rda')
save(Mod_9_60_hour_c, file = 'Mod_9_60_hour_c.Rda')
save(Mod_9_60_hour_f, file = 'Mod_9_60_hour_f.Rda')
save(Mod_9_60_hour_sin, file = 'Mod_9_60_hour_sin.Rda')
save(Mod_9_60_week_c, file = 'Mod_9_60_week_c.Rda')
save(Mod_9_60_week_f, file = 'Mod_9_60_week_f.Rda')
save(Mod_9_60_week_sin, file = 'Mod_9_60_week_sin.Rda')
save(Mod_9_60_week_sin_2, file = 'Mod_9_60_week_sin_2.Rda')
save(Mod_9_60_week_sin_3, file = 'Mod_9_60_week_sin_3.Rda')
save(Mod_9_60_month_c, file = 'Mod_9_60_month_c.Rda')
save(Mod_9_60_month_f, file = 'Mod_9_60_month_f.Rda')
save(Mod_9_60_month_sin, file = 'Mod_9_60_month_sin.Rda')
save(Mod_9_60_season_c, file = 'Mod_9_60_season_c.Rda')
save(Mod_9_60_season_f, file = 'Mod_9_60_season_f.Rda')
save(Mod_9_60_season_sin, file = 'Mod_9_60_season_sin.Rda')

save(Mod_9_60_NWP1, file = 'Mod_9_60_NWP1.Rda')
save(Mod_9_60_NWP2, file = 'Mod_9_60_NWP2.Rda')
save(Mod_9_60_climatology, file = 'Mod_9_60_climatology.Rda')
```

```{r}
Mod_9_60_inter = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_year_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ year')
Mod_9_60_year_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(year)')

Mod_9_60_hour_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ hour')
Mod_9_60_hour_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(hour)')
Mod_9_60_hour_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * hour/4) + sin(2*pi * hour/4)')

Mod_9_60_week_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ week')
Mod_9_60_week_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(week)')
Mod_9_60_week_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/52) + sin(2*pi * week/52)')
Mod_9_60_week_sin_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/53) + sin(2*pi * week/53)')
Mod_9_60_week_sin_3 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/52.5) + sin(2*pi * week/52.5)')

Mod_9_60_month_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ month')
Mod_9_60_month_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(month)')
Mod_9_60_month_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * month/12) + sin(2*pi * month/12)')

Mod_9_60_season_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ season')
Mod_9_60_season_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(season)')
Mod_9_60_season_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * season/4) + sin(2*pi * season/4)')

```


```{r}
plot_func = function(function_list = c(),
                     legend_input= c('Climatology', '1 NWP pred', '2 NWP preds'),
                     title = '',
                     lead_time_interval = c(1,240),
                     climatology_ref = FALSE){
    low = 1
    upp = 240
    ax = pretty(low:upp, 9)
    cols = c('black', 'brown1', 'dodgerblue1', 'orange')
    dat = get(function_list[1])
    if (climatology_ref==TRUE){
        plot_data = dat$Results[, .(mean_test_loss = mean(clima_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>low & lead_time <upp,mean(clima_loss)])
    } else{
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>lead_time_interval[1] & lead_time <lead_time_interval[2],mean(test_loss)])
    }
    matplot(low:upp, plot_data[low:upp,mean_test_loss] , type = 'l', ylim = c(0, 25), lty = 1,
            xaxt = 'n', xlab = 'Horizon (days)', ylab = 'Pinball loss', main = paste0(title,': 60 day window (Test)'), col = cols[1])
    legend("left", lty = 1, cex=0.6, col = c('black', 'brown1', 'dodgerblue1'),
           legend = legend_input)
    axis(1, at = ax, labels = ax/4)
    
    for (i in 2:length(function_list)){
        dat = get(function_list[i])
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>lead_time_interval[1] & lead_time <lead_time_interval[2],mean(test_loss)])
        matlines(low:upp, plot_data[low:upp,mean_test_loss], col = cols[i], lty = ifelse(i==2, 1, 2))
    }
}



plot_month = function(function_list = c(),
                     legend_input= c('Climatology', '1 NWP pred', '2 NWP preds'),
                     title = '',
                     climatology_ref = FALSE){
    low = 1
    upp = 12
    ax = month.abb
    cols = c('black', 'brown1', 'dodgerblue1', 'orange')
    dat = get(function_list[1])
    if (climatology_ref==TRUE){
        plot_data = dat$Results[lead_time<81, .(mean_test_loss = mean(clima_loss)), keyby=.(horizon =month(date))]
    } else{
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =month(date))]
    }
    matplot(low:upp, plot_data[low:upp,mean_test_loss] , type = 'l', ylim = c(0, 25), lty = 1,
            xaxt = 'n', xlab = 'Month', ylab = 'Pinball loss', main = paste0(title,': 60 day window (Test)'), col = cols[1])
    legend("left", lty = 1, cex=0.6, col = c('black', 'brown1', 'dodgerblue1'),
           legend = legend_input)
    axis(1, at = 1:12, labels = ax)
    
    for (i in 2:length(function_list)){
        dat = get(function_list[i])
        plot_data = dat$Results[lead_time<81, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =month(date))]
        matlines(low:upp, plot_data[low:upp,mean_test_loss], col = cols[i], lty = ifelse(i==2, 1, 2))
    }
}
```


```{r}
plot_func(c('Mod_9_60_inter', 'Mod_9_60_year_c', 'Mod_9_60_year_f'),
          legend_input = c('Intercept', 'Year (cont)', 'Year (factor)'))
plot_func(c('Mod_9_60_hour_c', 'Mod_9_60_hour_f', 'Mod_9_60_hour_sin'))
plot_func(c('Mod_9_60_week_c', 'Mod_9_60_week_f', 'Mod_9_60_week_sin', 'Mod_9_60_week_sin_2','Mod_9_60_week_sin_3'))
plot_func(c('Mod_9_60_month_c', 'Mod_9_60_month_f', 'Mod_9_60_month_sin'))
plot_func(c('Mod_9_60_season_c', 'Mod_9_60_season_f', 'Mod_9_60_season_sin'))
```

1) Continuos year is better 22.44 (Almost same as intercept) 
2) hour as factor better 22.1 (almost same as intercept)
3) Cont week is hopeless, as factor good, best is 52 weeks of  9.96
4) Month as factor is better 10.48
5) Season as factor 13.48

# Trying climatology and NWP vars
```{r}
Mod_9_60_NWP1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_NWP2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_climatology = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)
```



```{r}
plot_func(c('Mod_9_60_climatology','Mod_9_60_NWP1', 'Mod_9_60_NWP2'), 
          title = 'Intercept + NWP1 + NWP2', climatology_ref = TRUE)
plot_month(c('Mod_9_60_climatology','Mod_9_60_NWP1', 'Mod_9_60_NWP2'), 
          title = 'Intercept + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80
```

1) climatology is very good, 
2) there seems to be pretty good skill
3) we are doing better in winter than in summer. 
4) Virtually no skill using information from previous month NWP2. 
5) Can we improve model with the time covariates?

# Time covariate models
```{r}
Mod_9_60_comb_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_a_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_a_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

```



as.factor(month) +  as.factor(season) leads to an undefined matrix, so we have to go with an alternative. 


# Interaction models
```{r}
Mod_9_60_int_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(season)')
Mod_9_60_int_b_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month)')
Mod_9_60_int_c_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week)')
```

# Plot
```{r}
plot_func(c('Mod_9_60_comb_a_0','Mod_9_60_comb_a_1', 'Mod_9_60_comb_a_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE,
          lead_time_interval = c(0, 4*15))
plot_month(c('Mod_9_60_comb_a_0','Mod_9_60_comb_a_1', 'Mod_9_60_comb_a_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE) # lead_time< 80

plot_func(c('Mod_9_60_int_a_0','Mod_9_60_int_b_0', 'Mod_9_60_int_c_0'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE,
          lead_time_interval = c(0, 4*15))
plot_month(c('Mod_9_60_int_a_0','Mod_9_60_int_b_0', 'Mod_9_60_int_c_0'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE) # lead_time< 80
```
1) This is a better climatology than using the quantile directly. 
2) Including the NWP2 very slightly increases the performance of the model.
3) This increase comes at the beginning, so it seems worth it. 


```{r}
Mod_9_60_comb_int_c_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
Mod_9_60_comb_int_c_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
Mod_9_60_comb_int_c_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

```
1) Here we cannot run week and sin(week) together. 

```{r}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_c_0','Mod_9_60_comb_int_c_1', 'Mod_9_60_comb_int_c_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = TRUE)
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_c_0','Mod_9_60_comb_int_c_1', 'Mod_9_60_comb_int_c_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80


```

#Interactions worsens the NWP models


save(Mod_9_60_comb_int_c_0, file = 'Mod_9_60_comb_int_c_0.Rda')
save(Mod_9_60_comb_int_c_1, file = 'Mod_9_60_comb_int_c_1.Rda')
save(Mod_9_60_comb_int_c_2, file = 'Mod_9_60_comb_int_c_2.Rda')



scp eirikhsj@abacus-as.uio.no:~/Mod_9_60_comb_int_c_0.Rda eirikhsj@abacus-as.uio.no:~/Mod_9_60_comb_int_c_1.Rda eirikhsj@abacus-as.uio.no:~/Mod_9_60_comb_int_c_2.Rda  /Users/Eirik/Desktop/Master2023/Output_data/New_Best_NWP_model_output


eirikhsj@abacus-as.uio.no:/mn/kadingir/datascience_000000/eirikhsj



```{r}
M_9_60_0       = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', window = 60, cores = 48)
M_9_60_1       = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', window = 60, cores = 48)
M_9_60_2       = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', window = 60, cores = 48)

M_9_60_0_h     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', window = 60, hour_v = TRUE, cores = 48)
M_9_60_1_h     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', window = 60, hour_v = TRUE, cores = 48)
M_9_60_2_h     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', window = 60, hour_v = TRUE, cores = 48) 

M_9_60_0_w     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', window = 60, week_v = TRUE, cores = 48)
M_9_60_1_w     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', window = 60, week_v = TRUE, cores = 48)
M_9_60_2_w     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', window = 60, week_v = TRUE, cores = 48)

M_9_60_0_m     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', window = 60, month_v = TRUE, cores = 48)
M_9_60_1_m     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', window = 60, month_v = TRUE, cores = 48)
M_9_60_2_m     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', window = 60, month_v = TRUE, cores = 48) 

M_9_60_0_y     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', window = 60, year_v = TRUE, cores = 48)
M_9_60_1_y     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', window = 60, year_v = TRUE, cores = 48)
M_9_60_2_y     = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', window = 60, year_v = TRUE, cores = 48) 
```

