---
title: "Best NWP FINAL"
author: "Eirik Sjåvik"
date: "2023-03-06"
output: html_document
---


```{r, cache = TRUE}
library(DemandForecast)
library(data.table)
library(ncdf4)
library(parallel)
library(mgcv)
library(quantreg)

ERA_NWP = get_ERA_NWP(ERA_path = "/mn/kadingir/datascience_000000/eirikhsj/PC_ERA_79_92.Rda", 
                      NWP_path ="/mn/kadingir/datascience_000000/eirikhsj/NWP_quant_1993_2023.Rda",
                      quant = "90", reweight = FALSE)

ERA_NWP[, season:= ifelse(month(date) %in% c(12,1,2), 1, 
                            ifelse(month(date) %in% c(3,4,5), 2,
                            ifelse(month(date) %in% c(6,7,8), 3, 4)))]




```

```{r, eval  = FALSE}
save(Mod_9_60_inter, file = 'Mod_9_60_inter.Rda')
save(Mod_9_60_year_c, file = 'Mod_9_60_year_c.Rda')
save(Mod_9_60_year_f, file = 'Mod_9_60_year_f.Rda')
save(Mod_9_60_hour_c, file = 'Mod_9_60_hour_c.Rda')
save(Mod_9_60_hour_f, file = 'Mod_9_60_hour_f.Rda')
save(Mod_9_60_hour_sin, file = 'Mod_9_60_hour_sin.Rda')
save(Mod_9_60_week_c, file = 'Mod_9_60_week_c.Rda')
save(Mod_9_60_week_f, file = 'Mod_9_60_week_f.Rda')
save(Mod_9_60_week_sin, file = 'Mod_9_60_week_sin.Rda')
save(Mod_9_60_week_sin_2, file = 'Mod_9_60_week_sin_2.Rda')
save(Mod_9_60_week_sin_3, file = 'Mod_9_60_week_sin_3.Rda')
save(Mod_9_60_month_c, file = 'Mod_9_60_month_c.Rda')
save(Mod_9_60_month_f, file = 'Mod_9_60_month_f.Rda')
save(Mod_9_60_month_sin, file = 'Mod_9_60_month_sin.Rda')
save(Mod_9_60_season_c, file = 'Mod_9_60_season_c.Rda')
save(Mod_9_60_season_f, file = 'Mod_9_60_season_f.Rda')
save(Mod_9_60_season_sin, file = 'Mod_9_60_season_sin.Rda')

save(Mod_9_60_NWP1, file = 'Mod_9_60_NWP1.Rda')
save(Mod_9_60_NWP2, file = 'Mod_9_60_NWP2.Rda')
save(Mod_9_60_climatology, file = 'Mod_9_60_climatology.Rda')

save(Mod_9_60_comb_a_0, file = 'Mod_9_60_comb_a_0.Rda')
save(Mod_9_60_comb_a_1, file = 'Mod_9_60_comb_a_1.Rda') 
save(Mod_9_60_comb_a_2, file = 'Mod_9_60_comb_a_2.Rda') 

save(Mod_9_60_int_a_0, file = 'Mod_9_60_int_a_0.Rda')
save(Mod_9_60_int_b_0, file = 'Mod_9_60_int_b_0.Rda')
save(Mod_9_60_int_c_0, file = 'Mod_9_60_int_c_0.Rda')

save(Mod_9_60_comb_int_c_0, file = 'Mod_9_60_comb_int_c_0.Rda')
save(Mod_9_60_comb_int_c_1, file = 'Mod_9_60_comb_int_c_1.Rda')
save(Mod_9_60_comb_int_c_2, file = 'Mod_9_60_comb_int_c_2.Rda')
save(Mod_9_60_comb_int_b_0, file = 'Mod_9_60_comb_int_b_0.Rda')
save(Mod_9_60_comb_int_b_1, file = 'Mod_9_60_comb_int_b_1.Rda')
save(Mod_9_60_comb_int_b_2, file = 'Mod_9_60_comb_int_b_2.Rda')
save(Mod_9_60_comb_int_a_0, file = 'Mod_9_60_comb_int_b_0.Rda')
save(Mod_9_60_comb_int_a_1, file = 'Mod_9_60_comb_int_a_1.Rda')
save(Mod_9_60_comb_int_a_2, file = 'Mod_9_60_comb_int_a_2.Rda')
save(Mod_9_60_comb_hour_1, file = 'Mod_9_60_comb_hour_1')
save(Mod_9_60_comb_hour_2, file = 'Mod_9_60_comb_hour_2')
save(Mod_9_60_comb_week_1, file = 'Mod_9_60_comb_week_1')
save(Mod_9_60_comb_week_2, file = 'Mod_9_60_comb_week_2')




```
,(?<=\,)(.*?)(?=\))


```{r, cache = TRUE}
path = "~/Desktop/Master2023/Data/Output_data/New_Best_NWP_model_output/"
load(paste0(path, Mod_9_60_inter,".Rda"))
load(paste0(path, Mod_9_60_year_c,".Rda"))
load(paste0(path, Mod_9_60_year_f,".Rda"))
load(paste0(path, Mod_9_60_hour_c,".Rda"))
load(paste0(path, Mod_9_60_hour_f,".Rda"))
load(paste0(path, Mod_9_60_hour_sin,".Rda"))
load(paste0(path, Mod_9_60_week_c,".Rda"))
load(paste0(path, Mod_9_60_week_f,".Rda"))
load(paste0(path, Mod_9_60_week_sin,".Rda"))
load(paste0(path, Mod_9_60_week_sin_2,".Rda"))
load(paste0(path, Mod_9_60_week_sin_3,".Rda"))
load(paste0(path, Mod_9_60_month_c,".Rda"))
load(paste0(path, Mod_9_60_month_f,".Rda"))
load(paste0(path, Mod_9_60_month_sin,".Rda"))
load(paste0(path, Mod_9_60_season_c,".Rda"))
load(paste0(path, Mod_9_60_season_f,".Rda"))
load(paste0(path, Mod_9_60_season_sin,".Rda"))
load(paste0(path, Mod_9_60_NWP1,".Rda"))
load(paste0(path, Mod_9_60_NWP2,".Rda"))
load(paste0(path, Mod_9_60_climatology,".Rda"))

load(paste0(path, Mod_9_60_comb_a_0,".Rda"))
load(paste0(path, Mod_9_60_comb_a_1,".Rda")) 
load(paste0(path, Mod_9_60_comb_a_2,".Rda"))

load(paste0(path, Mod_9_60_int_a_0,".Rda"))
load(paste0(path, Mod_9_60_int_b_0,".Rda"))
load(paste0(path, Mod_9_60_int_c_0,".Rda"))

load(paste0(path, Mod_9_60_comb_int_c_0,".Rda"))
load(paste0(path, Mod_9_60_comb_int_c_1,".Rda"))
load(paste0(path, Mod_9_60_comb_int_c_2,".Rda"))

load(paste0(path, Mod_9_60_comb_int_b_0,".Rda"))
load(paste0(path, Mod_9_60_comb_int_b_1,".Rda"))
load(paste0(path, Mod_9_60_comb_int_b_2,".Rda"))

load(paste0(path, Mod_9_60_comb_int_a_0,".Rda"))
load(paste0(path, Mod_9_60_comb_int_a_1,".Rda"))
load(paste0(path, Mod_9_60_comb_int_a_2,".Rda"))

load(paste0(path, Mod_9_60_comb_hour_1,".Rda"))
load(paste0(path, Mod_9_60_comb_hour_2,".Rda"))

load(paste0(path, Mod_9_60_comb_week_1,".Rda"))
load(paste0(path, Mod_9_60_comb_week_2,".Rda"))


load(paste0(path, Mod_9_120_NWP2,".Rda"))
load(paste0(path, Mod_9_120_NWP1,".Rda"))
load(paste0(path, Mod_9_120_climatology,".Rda"))
```

```{r, eval = FALSE}
Mod_9_60_inter = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_year_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ year')
Mod_9_60_year_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(year)')

Mod_9_60_hour_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ hour')
Mod_9_60_hour_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(hour)')
Mod_9_60_hour_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * hour/4) + sin(2*pi * hour/4)')

Mod_9_60_week_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ week')
Mod_9_60_week_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(week)')
Mod_9_60_week_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/52) + sin(2*pi * week/52)')
Mod_9_60_week_sin_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/53) + sin(2*pi * week/53)')
Mod_9_60_week_sin_3 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * week/52.5) + sin(2*pi * week/52.5)')

Mod_9_60_month_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ month')
Mod_9_60_month_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(month)')
Mod_9_60_month_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * month/12) + sin(2*pi * month/12)')

Mod_9_60_season_c = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ season')
Mod_9_60_season_f = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ as.factor(season)')
Mod_9_60_season_sin = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                     window = 60, cores = 48, formula  = 'PC1 ~ cos(2*pi * season/4) + sin(2*pi * season/4)')

```

## Plotting functions
```{r, cache = TRUE}
plot_func = function(function_list = c(),
                     legend_input= c('Climatology', '1 NWP pred', '2 NWP preds'),
                     title = '',
                     lead_time_interval = c(1,240),
                     climatology_ref = FALSE,
                     legend_place = 'top'){
    low = 1
    upp = 240
    ax = pretty(low:upp, 9)
    cols = c('black', 'brown1', 'dodgerblue1', 'orange', 'green')
    dat = get(function_list[1])
    if (climatology_ref==TRUE){
        plot_data = dat$Results[, .(mean_test_loss = mean(clima_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>=lead_time_interval[1] & lead_time <=lead_time_interval[2],mean(clima_loss)])
    } else{
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>=lead_time_interval[1] & lead_time <=lead_time_interval[2],mean(test_loss)])
    }
    matplot(low:upp, plot_data[low:upp,mean_test_loss] , type = 'l', ylim = c(0, 25), lty = 1,
            xaxt = 'n', xlab = 'Horizon (days)', ylab = 'Pinball loss', main = paste0(title,': 60 day window (Test)'), col = cols[1])
    legend(legend_place, lty = 1, cex=0.6, col = c('black', 'brown1', 'dodgerblue1', 'orange', 'green'),
           legend = legend_input)
    axis(1, at = ax, labels = ax/4)
    
    for (i in 2:length(function_list)){
        dat = get(function_list[i])
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =lead_time)]
        print(dat$Results[lead_time>=lead_time_interval[1] & lead_time <=lead_time_interval[2],mean(test_loss)])
        matlines(low:upp, plot_data[low:upp,mean_test_loss], col = cols[i], lty = ifelse(i==2, 1, 2))
    }
}



plot_month = function(function_list = c(),
                     legend_input= c('Climatology', '1 NWP pred', '2 NWP preds'),
                     title = '',
                     climatology_ref = FALSE,
                     legend_place = 'top'){
    low = 1
    upp = 12
    ax = month.abb
    cols = c('black', 'brown1', 'dodgerblue1', 'orange', 'green')
    dat = get(function_list[1])
    if (climatology_ref==TRUE){
        plot_data = dat$Results[, .(mean_test_loss = mean(clima_loss)), keyby=.(horizon =month(date))]
    } else{
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =month(date))]
    }
    matplot(low:upp, plot_data[low:upp,mean_test_loss] , type = 'l', ylim = c(0, 25), lty = 1,
            xaxt = 'n', xlab = 'Month', ylab = 'Pinball loss', main = paste0(title,': 60 day window (Test)'), col = cols[1])
    legend(legend_place, lty = 1, cex=0.6, col = c('black', 'brown1', 'dodgerblue1', 'orange', 'green'),
           legend = legend_input)
    axis(1, at = 1:12, labels = ax)
    
    for (i in 2:length(function_list)){
        dat = get(function_list[i])
        plot_data = dat$Results[, .(mean_test_loss = mean(test_loss)), keyby=.(horizon =month(date))]
        matlines(low:upp, plot_data[low:upp,mean_test_loss], col = cols[i], lty = ifelse(i==2, 1, 2))
    }
}
```


```{r, cache=TRUE}
plot_func(c('Mod_9_60_inter', 'Mod_9_60_year_c', 'Mod_9_60_year_f'),
          legend_input = c('Intercept', 'Year (cont)', 'Year (factor)'), legend_place = 'bottomright')
plot_func(c('Mod_9_60_hour_c', 'Mod_9_60_hour_f', 'Mod_9_60_hour_sin'), legend_place = 'bottomright',
          title = 'Hour', legend_input = c('Hour (cont)', 'Hour (factor)', 'Hour sinusoidal'))
plot_func(c('Mod_9_60_week_c', 'Mod_9_60_week_f', 'Mod_9_60_week_sin', 'Mod_9_60_week_sin_2','Mod_9_60_week_sin_3'), legend_place = 'bottomright',
          title = 'Week', legend_input = c('Week (cont)', 'Week (factor)', 'Week sinusoidal(52)','Week sinusoidal(53)','Week sinusoidal(52.5)'))
plot_func(c('Mod_9_60_month_c', 'Mod_9_60_month_f', 'Mod_9_60_month_sin'), legend_place = 'bottomright',
           title = 'Month', legend_input = c('Month (cont)', 'Month (factor)', 'Month sinusoidal'))
plot_func(c('Mod_9_60_season_c', 'Mod_9_60_season_f', 'Mod_9_60_season_sin'), legend_place = 'bottomright',
          title = 'Season', legend_input = c('Season (cont)', 'Season (factor)', 'Season sinusoidal'))
```

1) Continuous year is better 22.44 (Almost same as intercept) 
2) hour as factor better 22.1 (almost same as intercept)
3) Cont week is hopeless, as factor good, best is 52 weeks of  9.96
4) Month as factor is better 10.48
5) Season as factor 13.48

# Trying climatology and NWP vars
```{r, eval=FALSE}
Mod_9_60_NWP1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_NWP2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1')
Mod_9_60_climatology = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1', incl_climatology = TRUE)
```


```{r, cahce = TRUE}
plot_func(c('Mod_9_60_climatology','Mod_9_60_NWP1', 'Mod_9_60_NWP2'), 
          title = 'Climatology + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology','Mod_9_60_NWP1', 'Mod_9_60_NWP2'), 
          title = 'Climatology + NWP1 + NWP2', climatology_ref = TRUE) 
```

1) climatology is very good, 
2) there seems to be pretty good 
3) we are doing better in winter than in summer. 
4) Virtually no skill using information from previous month NWP2. 
5) Can we improve model with the time covariates?

# Time covariate models
```{r, eval = FALSE}
Mod_9_60_comb_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_a_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg',window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_a_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
```


as.factor(month) +  as.factor(season) leads to an undefined matrix, so we have to go with an alternative. 

```{r, cache = TRUE}
plot_func(c('Mod_9_60_comb_a_0','Mod_9_60_comb_a_1', 'Mod_9_60_comb_a_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE,legend_input= c('Time covariates', '+ 1 NWP', '+ 2 NWP'),lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_comb_a_0','Mod_9_60_comb_a_1', 'Mod_9_60_comb_a_2'), 
          title = 'Time combo + NWP1 + NWP2', climatology_ref = FALSE,legend_input= c('Time covariates', '+ 1 NWP', '+ 2 NWP')) 
```
1) This is a better climatology than using the quantile directly. 9.04
2) Including the NWP2 very slightly increases the performance of the model. 8.11 vs 8.19 overall
3) This increase comes at the beginning, so it seems worth it, contributes the first 10 days, 

first 10 days is 5.78 vs 5.13
first 20 days is 6.27 vs 6.41
first 30 days is 7.45 vs 7.27

days 10-20 i 7.6550 vs 7.6658

We can again outperform the climatology model on a predictive task by using time covariates.

# Interaction models
```{r, eval = FALSE}
Mod_9_60_int_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(season)')
Mod_9_60_int_b_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month)')
Mod_9_60_int_c_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week)')
```

# Plot
```{r, cache = TRUE}
plot_func(c('Mod_9_60_int_a_0','Mod_9_60_int_b_0', 'Mod_9_60_int_c_0'), 
          title = 'Interactions hour with season, month week', climatology_ref = FALSE,
          legend_input= c('Hour:Season', 'Hour:Month', 'Hour:Week'))
plot_month(c('Mod_9_60_int_a_0','Mod_9_60_int_b_0', 'Mod_9_60_int_c_0'), 
          title = 'Interactions hour with season, month week', climatology_ref = FALSE,
          legend_input= c('Hour:Season', 'Hour:Month', 'Hour:Week')) 
```
1) Hour:Week is the best one, and a better model than climatology. 


```{r}
Mod_9_60_comb_int_c_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
Mod_9_60_comb_int_c_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
Mod_9_60_comb_int_c_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', 
                                      window = 60, cores = 48, formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(week) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

```
1) Here we cannot run week and sin(week) together. 

```{r}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_c_0','Mod_9_60_comb_int_c_1', 'Mod_9_60_comb_int_c_2'), 
          title = 'Interaction hour:week + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_c_0','Mod_9_60_comb_int_c_1', 'Mod_9_60_comb_int_c_2'), 
          title = 'Interaction hour:week + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80
```
-Interactions worsens the NWP models


```{r, eval = FALSE}
Mod_9_60_comb_int_b_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', 
                                      window = 60, cores = 48, 
                                      formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month) + cos(2*pi * week/52) + sin(2*pi * week/52) + year')
Mod_9_60_comb_int_b_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg', 
                                      window = 60, cores = 48, 
                                      formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month) + cos(2*pi * week/52) + sin(2*pi * week/52) + year')
Mod_9_60_comb_int_b_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', 
                                      window = 60, cores = 48, 
                                      formula  = 'PC1 ~ 1 + as.factor(hour)*as.factor(month) + cos(2*pi * week/52) + sin(2*pi * week/52) + year')
```

```{r, cahce = TRUE}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_b_0','Mod_9_60_comb_int_b_1', 'Mod_9_60_comb_int_b_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_b_0','Mod_9_60_comb_int_b_1', 'Mod_9_60_comb_int_b_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80
```


```{r, eval = FALSE}
Mod_9_60_comb_int_a_0 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 0, model = 'reg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season) + cos(2*pi * week/52) + sin(2*pi * week/52) + 
                                    cos(2*pi * month/12) + sin(2*pi * month/12) +as.factor(season) + year')

Mod_9_60_comb_int_a_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg',window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season)  + cos(2*pi * week/52) + 
                                    sin(2*pi * week/52) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')

Mod_9_60_comb_int_a_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg', window = 60, cores = 48, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour):as.factor(season)  + cos(2*pi * week/52) + 
                                    sin(2*pi * week/52) + cos(2*pi * month/12) + sin(2*pi * month/12) + as.factor(season) + year')
```

```{r, cache=TRUE}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_a_0','Mod_9_60_comb_int_a_1', 'Mod_9_60_comb_int_a_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_int_a_0','Mod_9_60_comb_int_a_1', 'Mod_9_60_comb_int_a_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE) # lead_time< 80
```




So based on this is seems that the best model is the one with just the NWP, at least for the first 20 days. 
Might be interesting to check if we can add hour and week a simpler comb model basically. 

```{r}
Mod_9_60_comb_hour_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour)')

Mod_9_60_comb_hour_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(hour)')

```


```{r}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_hour_1','Mod_9_60_comb_hour_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_hour_1','Mod_9_60_comb_hour_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE) 
```

```{r}
Mod_9_60_comb_week_1 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 1, model = 'reg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(week)')

Mod_9_60_comb_week_2 = rolling_mod_NWP('2007-01-01', '2023-01-31', 0.9, ERA_NWP, 2, model = 'reg',window = 60, cores = 4, 
                                    formula  = 'PC1 ~ 1 + as.factor(week)')
```

```{r}
plot_func(c('Mod_9_60_climatology', 'Mod_9_60_comb_week_1','Mod_9_60_comb_week_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE,lead_time_interval = c(1,240))
plot_month(c('Mod_9_60_climatology', 'Mod_9_60_comb_week_1','Mod_9_60_comb_week_2'), 
          title = 'Interaction hour:month + NWP1 + NWP2', climatology_ref = TRUE) 
```



```{r}
Mod_9_60_climatology_daily = Mod_9_60_climatology$Results[,.(daily_pca =mean(PC1), daily_pred =mean(clima_pred)), by = .(init_date, date)]
Mod_9_60_climatology_daily[, daily_loss := pinball_loss(0.9, daily_pred,daily_pca)]
Mod_9_60_climatology_daily[, lead_time := as.integer(date - init_date) + 1]

plot(Mod_9_60_climatology_daily[,mean(daily_loss), by = lead_time], type = 'l')

Mod_9_60_NWP1_daily = Mod_9_60_NWP1$Results[,.(daily_pca =mean(PC1), daily_pred =mean(pred)), by = .(init_date, date)]
Mod_9_60_NWP1_daily[, daily_loss := pinball_loss(0.9, daily_pred,daily_pca)]
Mod_9_60_NWP1_daily[, lead_time := as.integer(date - init_date) + 1]

plot(Mod_9_60_climatology_daily[,mean(daily_loss), by = lead_time], type = 'l',col = 'red', ylim = c(0, 12))
lines(Mod_9_60_NWP1_daily[,mean(daily_loss), by = lead_time])
par(new= TRUE)
plot(Mod_9_60_climatology$Results[,mean(clima_loss), by = lead_time], type = 'l',col = 'blue', ylim = c(0, 12),axes = FALSE)
lines(Mod_9_60_NWP1$Results[,mean(test_loss), by = lead_time], col = 'green')

plot(1 - (Mod_9_60_NWP1_daily[,mean(daily_loss), by = lead_time][,V1]/
    Mod_9_60_climatology_daily[,mean(daily_loss), by = lead_time][,V1]),
              type = 'l', ylim = c(-0.1, 1))
par(new =TRUE)
plot(1 - (Mod_9_60_NWP1$Results[,mean(test_loss), by = lead_time][,V1]/
              Mod_9_60_climatology$Results[,mean(clima_loss), by = lead_time][,V1]),
              type = 'l',col = 'blue', ylim = c(-0.1, 1),axes = FALSE)

#By 7 days
Mod_9_60_climatology_weekly = Mod_9_60_climatology$Results[,.(daily_pca =sum(PC1), daily_pred =sum(clima_pred)), by = .(init_date, week(date))]

```


# Considering different prediction intervals (daily prediction)
```{r, cache = TRUE}

Mod_9_120_climatology$Results[, clima_loss := pinball_loss(0.9, clima_pred,PC1)]

#Making interval groups 1-days
Mod_9_120_climatology$Results[, group1 := (lead_time-1)%/%4]
Mod_9_120_climatology$Results[, c("PC_1days", "mean1days"):= .(mean(PC1),  mean(clima_pred)), by = .(group1, init_date)]
Mod_9_120_climatology$Results[, loss1days := pinball_loss(0.9, mean1days,PC_1days)]

Mod_9_120_NWP1$Results[, group1 := (lead_time-1)%/%4]
Mod_9_120_NWP1$Results[, c("PC_1days", "mean1days"):= .(mean(PC1),  mean(pred)), by = .(group1, init_date)]
Mod_9_120_NWP1$Results[, loss1days := pinball_loss(0.9, mean1days,PC_1days)]
plot(Mod_9_120_NWP1$Results[, mean(loss1days), by = group1], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_climatology$Results[, mean(loss1days), by = group1], col = 'red')

#Making interval groups 2-days
Mod_9_120_climatology$Results[, group2 := (lead_time-1)%/%8]
Mod_9_120_climatology$Results[, c("PC_2days", "mean2days"):= .(mean(PC1),  mean(clima_pred)), by = .(group2, init_date)]
Mod_9_120_climatology$Results[, loss2days := pinball_loss(0.9, mean2days,PC_2days)]

Mod_9_120_NWP1$Results[, group2 := (lead_time-1)%/%8]
Mod_9_120_NWP1$Results[, c("PC_2days", "mean2days"):= .(mean(PC1),  mean(pred)), by = .(group2, init_date)]
Mod_9_120_NWP1$Results[, loss2days := pinball_loss(0.9, mean2days,PC_2days)]
plot(Mod_9_120_NWP1$Results[, mean(loss2days), by = group2], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_climatology$Results[, mean(loss2days), by = group2], col = 'red')

#Making interval groups 4-days
Mod_9_120_climatology$Results[, group4 := (lead_time-1)%/%16]
Mod_9_120_climatology$Results[, c("PC_4days", "mean4days"):= .(mean(PC1),  mean(clima_pred)), by = .(group4, init_date)]
Mod_9_120_climatology$Results[, loss4days := pinball_loss(0.9, mean4days,PC_4days)]

Mod_9_120_NWP1$Results[, group4 := (lead_time-1)%/%16]
Mod_9_120_NWP1$Results[, c("PC_4days", "mean4days"):= .(mean(PC1),  mean(pred)), by = .(group4, init_date)]
Mod_9_120_NWP1$Results[, loss4days := pinball_loss(0.9, mean4days,PC_4days)]
plot(Mod_9_120_NWP1$Results[, mean(loss4days), by = group4], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_climatology$Results[, mean(loss4days), by = group4], col = 'red')

#Making interval groups 8-days
Mod_9_120_climatology$Results[, group8 := (lead_time-1)%/%32]
Mod_9_120_climatology$Results[, c("PC_8days", "mean8days"):= .(mean(PC1),  mean(clima_pred)), by = .(group8, init_date)]
Mod_9_120_climatology$Results[, loss8days := pinball_loss(0.9, mean8days,PC_8days)]

Mod_9_120_NWP1$Results[, group8 := (lead_time-1)%/%32]
Mod_9_120_NWP1$Results[, c("PC_8days", "mean8days"):= .(mean(PC1),  mean(pred)), by = .(group8, init_date)]
Mod_9_120_NWP1$Results[, loss8days := pinball_loss(0.9, mean8days,PC_8days)]
plot(Mod_9_120_NWP1$Results[, mean(loss8days), by = group8], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_climatology$Results[, mean(loss8days), by = group8], col = 'red')

#Making interval groups 16-days
Mod_9_120_climatology$Results[, group16 := (lead_time-1)%/%64]
Mod_9_120_climatology$Results[, c("PC_16days", "mean16days"):= .(mean(PC1),  mean(clima_pred)), by = .(group16, init_date)]
Mod_9_120_climatology$Results[, loss16days := pinball_loss(0.9, mean16days,PC_16days)]

Mod_9_120_NWP1$Results[, group16 := (lead_time-1)%/%64]
Mod_9_120_NWP1$Results[, c("PC_16days", "mean16days"):= .(mean(PC1),  mean(pred)), by = .(group16, init_date)]
Mod_9_120_NWP1$Results[, loss16days := pinball_loss(0.9, mean16days,PC_16days)]
plot(Mod_9_120_NWP1$Results[, mean(loss16days), by = group16], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_climatology$Results[, mean(loss16days), by = group16], col = 'red')

#Making interval groups 32-days
Mod_9_120_climatology$Results[, group32 := (lead_time-1)%/%128]
Mod_9_120_climatology$Results[, c("PC_32days", "mean32days"):= .(mean(PC1),  mean(clima_pred)), by = .(group32, init_date)]
Mod_9_120_climatology$Results[, loss32days := pinball_loss(0.9, mean32days,PC_32days)]

Mod_9_120_NWP1$Results[, group32 := (lead_time-1)%/%128]
Mod_9_120_NWP1$Results[, c("PC_32days", "mean32days"):= .(mean(PC1),  mean(pred)), by = .(group32, init_date)]
Mod_9_120_NWP1$Results[, loss32days := pinball_loss(0.9, mean32days,PC_32days)]
plot(Mod_9_120_NWP1$Results[, mean(loss32days), by = group32], type = 'l', ylim = c(0, 12))
lines(Mod_9_120_climatology$Results[, mean(loss32days), by = group32], col = 'red')


```

```{r, cache = TRUE}
plot(1 - (Mod_9_120_NWP1$Results[,mean(test_loss), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(clima_loss), by = lead_time][,V1]),xaxt = 'n',
              type = 'l',col = rgb(0,0,0,0.5), lty = 2, ylim = c(-0.1, 0.6), main = "Skill by Period", xlab = "Lead Time (Days)", ylab = "Skill Score")
abline(h = 0)
lines(rep(1 - (Mod_9_120_NWP1$Results[,mean(loss1days), by = group1][,V1]/
              Mod_9_120_climatology$Results[,mean(loss1days), by = group1][,V1]), each = 4),col = 'grey')

lines(rep(1 - (Mod_9_120_NWP1$Results[,mean(loss2days), by = group2][,V1]/
               Mod_9_120_climatology$Results[,mean(loss2days), by = group2][,V1]), each = 8), col = 'grey')
lines(rep(1-  (Mod_9_120_NWP1$Results[,mean(loss4days), by = group4][,V1]/
              Mod_9_120_climatology$Results[,mean(loss4days), by = group4][,V1]), each = 16), col = 'grey')
lines(rep(1 - (Mod_9_120_NWP1$Results[,mean(loss8days), by = group8][,V1]/
              Mod_9_120_climatology$Results[,mean(loss8days), by = group8][,V1]), each = 32),col = 'red')
lines(rep(1 - (Mod_9_120_NWP1$Results[,mean(loss16days), by = group16][,V1]/
              Mod_9_120_climatology$Results[,mean(loss16days), by = group16][,V1]),each = 64),col = 'blue')
lines(rep(1 - (Mod_9_120_NWP1$Results[,mean(loss32days), by = group32][,V1]/
              Mod_9_120_climatology$Results[,mean(loss32days), by = group32][,V1]),each = 128),col = 'orange')
legend("topright", lty = 1, title = "Period:", cex = 1, pch = 16, col = c('black','grey','grey','grey', 'red', 'blue', 'orange'), legend = c("6-hour", "Daily", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
```



# Skill Interval Rolling mean version
```{r, cache = TRUE}
for (i in c(1,2,4,8,16,32)){
    Mod_9_120_climatology$Results[, c(paste0("PC_", i, "days_roll"), paste0("mean", i, "days_roll")):= .(rollapply(PC1, width = i*4, partial = TRUE, FUN = mean),rollapply(clima_pred, width = i*4, partial = TRUE, FUN = mean)), by = .(init_date)]
    Mod_9_120_climatology$Results[, paste0("loss", i, "days_roll") := pinball_loss(0.9,get(paste0("PC_", i, "days_roll")), get(paste0("mean", i, "days_roll")))]
    Mod_9_120_NWP1$Results[, c(paste0("PC_", i, "days_roll"), paste0("mean", i, "days_roll")):= .(rollapply(PC1, width = i*4, partial = TRUE, FUN = mean),  rollapply(pred, width = i*4, partial = TRUE, FUN = mean)), by = .(init_date)]
    Mod_9_120_NWP1$Results[, paste0("loss", i, "days_roll") := pinball_loss(0.9,get(paste0("PC_", i, "days_roll")), get(paste0("mean", i, "days_roll")))]
}

plot(1 - (Mod_9_120_NWP1$Results[,mean(test_loss), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(clima_loss), by = lead_time][,V1]),xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 2, ylim = c(-0.2, 0.8), main = "Skill by Period", xlab = "Lead Time (Days)", ylab = "Skill Score")
abline(h = 0)
lines(1 - (Mod_9_120_NWP1$Results[,mean(loss0.5days_roll), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(loss0.5days_roll), by = lead_time][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1$Results[,mean(loss1days_roll), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(loss1days_roll), by = lead_time][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1$Results[,mean(loss2days_roll), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(loss2days_roll), by = lead_time][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1$Results[,mean(loss4days_roll), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(loss4days_roll), by = lead_time][,V1]),col = 'grey')
lines(1 - (Mod_9_120_NWP1$Results[,mean(loss8days_roll), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(loss8days_roll), by = lead_time][,V1]),col = 'red')
lines(1 - (Mod_9_120_NWP1$Results[,mean(loss16days_roll), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(loss16days_roll), by = lead_time][,V1]),col = 'blue')
lines(1 - (Mod_9_120_NWP1$Results[,mean(loss32days_roll), by = lead_time][,V1]/
              Mod_9_120_climatology$Results[,mean(loss32days_roll), by = lead_time][,V1]),col = 'orange')

legend("topright", lty = 1, title = "Period:", cex = 1, pch = 16, col = c('black','grey','grey','grey','grey', 'red', 'blue', 'orange'), legend = c("6 hours", "12 hours","1 day", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))

```

```{r, cache = TRUE}
plot(Mod_9_120_NWP1$Results[,mean(test_loss), by = lead_time][,V1],xaxt = 'n',
              type = 'l',col = rgb(0,0,0,1), lty = 2, ylim = c(0,100), main = "Pinball Loss by Period", xlab = "Lead Time (Days)", ylab = "Pinball Loss")
abline(h = 0)
lines(Mod_9_120_NWP1$Results[,mean(loss0.5days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1$Results[,mean(loss1days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1$Results[,mean(loss2days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1$Results[,mean(loss4days_roll), by = lead_time][,V1],col = 'grey')
lines(Mod_9_120_NWP1$Results[,mean(loss8days_roll), by = lead_time][,V1],col = 'red')
lines(Mod_9_120_NWP1$Results[,mean(loss16days_roll), by = lead_time][,V1],col = 'blue')
lines(Mod_9_120_NWP1$Results[,mean(loss32days_roll), by = lead_time][,V1],col = 'orange')

legend("topright", lty = 1, title = "Period:", cex = 1, pch = 16, col = c('black','grey','grey','grey','grey', 'red', 'blue', 'orange'), legend = c("6 hours", "12 hours","1 day", "2 days", "4 days","8 days", "16 days", "32 days"))
axis(labels = c(1,20,40,60,80,100,120), side = 1, at = c(1,c(20,40,60,80,100,120)*4))
```


# Code for saving and relocating files

save(Mod_9_60_comb_int_a_0, file = 'Mod_9_60_comb_int_a_0.Rda')
save(Mod_9_60_comb_int_a_1, file = 'Mod_9_60_comb_int_a_1.Rda')
save(Mod_9_60_comb_int_a_2, file = 'Mod_9_60_comb_int_a_2.Rda')

scp eirikhsj@abacus-as.uio.no:~/Factor10_inter1.Rda eirikhsj@abacus-as.uio.no:~/Factor10_inter1_2.Rda eirikhsj@abacus-as.uio.no:~/Factor10_inter1_3.Rda eirikhsj@abacus-as.uio.no:~/Factor10_inter1_4.Rda eirikhsj@abacus-as.uio.no:~/Factor10_inter1_5.Rda eirikhsj@abacus-as.uio.no:~/Factor10_inter1_7.Rda eirikhsj@abacus-as.uio.no:~/Factor10_inter1_8.Rda 

/Users/Eirik/Desktop/Master2023/Output_data/


eirikhsj@abacus-as.uio.no:~/Factor10_inter1_6.Rda 
eirikhsj@abacus-as.uio.no:~/Factor10_inter1_9.Rda
eirikhsj@abacus-as.uio.no:~/Factor10_inter1_10.Rda

eirikhsj@abacus-as.uio.no:/mn/kadingir/datascience_000000/eirikhsj
