---
title: "Untitled"
author: "Eirik Sjåvik"
date: "2023-03-02"
output: html_document
---


# 4) Building best combination model 
```{r, eval = FALSE}
Naive= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                        p_comps = 0,  reg_form = "volume ~ hour + season + w_day + week + month + year")
```

## Best model no interaction
```{r}
No_inter_1= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour)  + as.factor(w_day) + s(week) + month1 + month2 + season1 + season2 + year")

No_inter_2= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(hour)  + as.factor(w_day) + s(week) + month1 + month2 + season1 + season2 + year")

No_inter_3= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour)  + as.factor(w_day) + as.factor(week) + month1 + month2 + season1 + season2 + year")

No_inter_4= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour)  + as.factor(w_day) + s(week) + s(month) + season1 + season2 + year", incl_climatology = TRUE)

No_inter_5= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour)  + as.factor(w_day) + s(week) + month1 + month2 + as.factor(season1)+ year")

##############
No_inter_6= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(hour)  + as.factor(w_day) + s(week) + s(month) + season1 + season2 + year")

No_inter_7= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour)  + as.factor(w_day) + as.factor(week) +s(month) + season1 + season2 + year")

No_inter_8= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour)  + as.factor(w_day) + s(week) + s(month) + as.factor(season1)+ year")
```


```{r, cache = TRUE}
plot(No_inter_1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(No_inter_2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(No_inter_3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(No_inter_4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')
lines(No_inter_5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(No_inter_6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(No_inter_5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(No_inter_7$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date])

plot(No_inter_1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(No_inter_2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(No_inter_3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(No_inter_4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')
lines(No_inter_5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(No_inter_6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(No_inter_7$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(No_inter_8$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = month(init_date)])

No_inter_1$Result[,sqrt(mean((volume - pred_1)^2))]
No_inter_2$Result[,sqrt(mean((volume - pred_1)^2))] 
No_inter_3$Result[,sqrt(mean((volume - pred_1)^2))] 
No_inter_4$Result[,sqrt(mean((volume - pred_1)^2))] #Best s(month)
No_inter_5$Result[,sqrt(mean((volume - pred_1)^2))]
No_inter_6$Result[,sqrt(mean((volume - pred_1)^2))]
No_inter_7$Result[,sqrt(mean((volume - pred_1)^2))]
No_inter_8$Result[,sqrt(mean((volume - pred_1)^2))]
Naive$Result[,sqrt(mean((volume - pred_1)^2))]
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```
```{r, cache = TRUE}
save(No_inter_1, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_1.Rda')
save(No_inter_2, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_2.Rda')
save(No_inter_3, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_3.Rda')
save(No_inter_4, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_4.Rda')
save(No_inter_5, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_5.Rda')
save(No_inter_6, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_6.Rda')
save(No_inter_7, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_7.Rda')
save(No_inter_8, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/No_inter_8.Rda')
save(Naive, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Naive.Rda')
```

## Interaction models
```{r}
Inter1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(week)  + as.factor(w_day):as.factor(week) + s(week) + s(month) + season1 + season2 + year")

Inter2 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(month)  + as.factor(w_day):as.factor(week) + s(week) + s(month) + season1 + season2 + year")

Inter3 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(week)  + as.factor(w_day):as.factor(month) + s(week) + s(month) + season1 + season2 + year") #Have run

Inter4 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(month)  + as.factor(w_day):as.factor(month) + s(week) + s(month) + season1 + season2 + year") #Have run
```


```{r, cache = TRUE}
plot(Inter1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(Inter2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Inter3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Inter4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')

lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date])

plot(Inter1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(Inter2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Inter3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Inter4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')

lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = month(init_date)])

Inter1$Result[pred_1<70000&pred_1>10000,sqrt(mean((volume - pred_1)^2))]
#Inter1$Result[,sqrt(mean((volume - pred_1)^2))]
Inter2$Result[,sqrt(mean((volume - pred_1)^2))] 
Inter3$Result[,sqrt(mean((volume - pred_1)^2))] 
Inter4$Result[,sqrt(mean((volume - pred_1)^2))] #Best s(month)

Naive$Result[,sqrt(mean((volume - pred_1)^2))]
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```


Inter1$Result[pred_1<70000&pred_1>10000,sqrt(mean((volume - pred_1)^2))]
Because of problems with overflow. 

## Single Factor loading models 
```{r, cache = TRUE}
Custom1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 1, custom = 's(PC1)',  reg_form = "volume ~ 1", cores =48)
Custom2 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 2, custom = 's(PC2)',  reg_form = "volume ~ 1", cores =48)
Custom3 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 3, custom = 's(PC3)',  reg_form = "volume ~ 1", cores =48)
Custom4= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps =4, custom = 's(PC4)',  reg_form = "volume ~ 1", cores =48)
Custom5 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 5, custom = 's(PC5)',  reg_form = "volume ~ 1", cores =48)
Custom6 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6, custom = 's(PC6)',  reg_form = "volume ~ 1", cores =48)
Custom7 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 7, custom = 's(PC7)',  reg_form = "volume ~ 1", cores =48)
Custom8 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 8, custom = 's(PC8)',  reg_form = "volume ~ 1", cores =48)
Custom9 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 9, custom = 's(PC9)',  reg_form = "volume ~ 1", cores =48)
Custom10 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10, custom = 's(PC10)',  reg_form = "volume ~ 1", cores =48)
```


```{r, cache = TRUE}
plot(Custom1$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Custom2$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom3$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom6$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom7$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom8$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom9$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom10$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date])

plot(Custom1$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Custom2$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom3$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom6$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom7$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom8$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom9$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom10$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = month(init_date)])

Custom1$Result[,sqrt(mean((volume - pred_2)^2))]
Custom2$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom3$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom4$Result[,sqrt(mean((volume - pred_2)^2))] #Best s(month)
Custom5$Result[,sqrt(mean((volume - pred_2)^2))]
Custom6$Result[,sqrt(mean((volume - pred_2)^2))]
Custom7$Result[,sqrt(mean((volume - pred_2)^2))]
Custom8$Result[,sqrt(mean((volume - pred_2)^2))]
Custom9$Result[,sqrt(mean((volume - pred_2)^2))]
Custom10$Result[,sqrt(mean((volume - pred_2)^2))]
Naive$Result[,sqrt(mean((volume - pred_1)^2))]
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```
```{r, cache = TRUE}
Custom_lin1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 1, custom = 'PC1',  reg_form = "volume ~ 1", cores =48)
Custom_lin2 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 2, custom = 'PC2',  reg_form = "volume ~ 1", cores =48)
Custom_lin3 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 3, custom = 'PC3',  reg_form = "volume ~ 1", cores =48)
Custom_lin4= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps =4, custom = 'PC4',  reg_form = "volume ~ 1", cores =48)
Custom_lin5 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 5, custom = 'PC5',  reg_form = "volume ~ 1", cores =48)
Custom_lin6 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6, custom = 'PC6',  reg_form = "volume ~ 1", cores =48)
Custom_lin7 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 7, custom = 'PC7',  reg_form = "volume ~ 1", cores =48)
Custom_lin8 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 8, custom = 'PC8',  reg_form = "volume ~ 1", cores =48)
Custom_lin9 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 9, custom = 'PC9',  reg_form = "volume ~ 1", cores =48)
Custom_lin10 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10, custom = 'PC10',  reg_form = "volume ~ 1", cores =48)
```

```{r, cache = TRUE}
plot(Custom_lin1$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Custom_lin2$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin3$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin6$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin7$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin8$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin9$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_lin10$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date])

plot(Custom_lin1$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Custom_lin2$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin3$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin6$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin7$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin8$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin9$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_lin10$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = month(init_date)])

Custom_lin1$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_lin2$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom_lin3$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom_lin4$Result[,sqrt(mean((volume - pred_2)^2))] #Best s(month)
Custom_lin5$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_lin6$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_lin7$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_lin8$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_lin9$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_lin10$Result[,sqrt(mean((volume - pred_2)^2))]
Naive$Result[,sqrt(mean((volume - pred_1)^2))]
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```



## Mean temperature model 
```{r, cache = TRUE}
Mean_temp1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 1, custom = 'hourly_mean_grid',  reg_form = "volume ~ 1")

Mean_temp2 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 1, custom = 's(hourly_mean_grid)',  reg_form = "volume ~ 1")
```

## Combinations of Factor loadings
```{r, cache = TRUE}
Custom_comb1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10,  reg_form = "volume ~ 1", cores =48)
Custom_comb2 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 2, custom = 's(PC1) + s(PC2)',  reg_form = "volume ~ 1", cores =48)
Custom_comb3 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 3, custom = 's(PC1) + s(PC3)',  reg_form = "volume ~ 1", cores =48)
Custom_comb4= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps =4, custom = 's(PC1) + s(PC4)',  reg_form = "volume ~ 1", cores =48)
Custom_comb5 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 5, custom = 's(PC1) + s(PC5)',  reg_form = "volume ~ 1", cores =48)
Custom_comb6 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6, custom = 's(PC1) + s(PC6)',  reg_form = "volume ~ 1", cores =48)
Custom_comb7 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 7, custom = 's(PC1) + s(PC7)',  reg_form = "volume ~ 1", cores =48)
Custom_comb8 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 8, custom = 's(PC1) + s(PC8)',  reg_form = "volume ~ 1", cores =48)
Custom_comb9 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 9, custom = 's(PC1) + s(PC9)',  reg_form = "volume ~ 1", cores =48)
Custom_comb10 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10, custom = 's(PC1) + s(PC10)',  reg_form = "volume ~ 1", cores =48)
```


save(Custom_comb1, file = 'Custom_comb1.Rda')
save(Custom_comb2, file = 'Custom_comb2.Rda')
save(Custom_comb3, file = 'Custom_comb3.Rda')
save(Custom_comb4, file = 'Custom_comb4.Rda')
save(Custom_comb5, file = 'Custom_comb5.Rda')
save(Custom_comb6, file = 'Custom_comb6.Rda')
save(Custom_comb7, file = 'Custom_comb7.Rda')
save(Custom_comb8, file = 'Custom_comb8.Rda')
save(Custom_comb9, file = 'Custom_comb9.Rda')
save(Custom_comb10, file = 'Custom_comb10.Rda')

scp eirikhsj@abacus-as.uio.no:~/Custom_comb1.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb2.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb3.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb4.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb5.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb6.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb7.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb8.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb9.Rda eirikhsj@abacus-as.uio.no:~/Custom_comb10.Rda /Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline

scp /Users/Eirik/Desktop/Master2023/Data/NWP_quant/NWP_quant_rew25_1993_2022.Rda eirikhsj@abacus-as.uio.no:/mn/kadingir/datascience_000000 


```{r, cache = TRUE}
plot(Custom_comb1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], col = 'red')
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_3)^2)), keyby = init_date])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_4)^2)), keyby = init_date])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_5)^2)), keyby = init_date])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_6)^2)), keyby = init_date])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_7)^2)), keyby = init_date])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_8)^2)), keyby = init_date])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_9)^2)), keyby = init_date])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_10)^2)), keyby = init_date])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date], col = 'blue')

plot(Custom_comb1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], col = 'red')
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_3)^2)), keyby = month(init_date)])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_4)^2)), keyby = month(init_date)])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_5)^2)), keyby = month(init_date)])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_6)^2)), keyby = month(init_date)])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_7)^2)), keyby = month(init_date)])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_8)^2)), keyby = month(init_date)])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_9)^2)), keyby = month(init_date)])
lines(Custom_comb1$Result[,sqrt(mean((volume - pred_10)^2)), keyby = month(init_date)])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = month(init_date)], col = 'blue')

Custom_comb1$Result[,sqrt(mean((volume - pred_1)^2))] 
Custom_comb1$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom_comb1$Result[,sqrt(mean((volume - pred_3)^2))] 
Custom_comb1$Result[,sqrt(mean((volume - pred_4)^2))]
Custom_comb1$Result[,sqrt(mean((volume - pred_5)^2))]
Custom_comb1$Result[,sqrt(mean((volume - pred_6)^2))]
Custom_comb1$Result[,sqrt(mean((volume - pred_7)^2))]
Custom_comb1$Result[,sqrt(mean((volume - pred_8)^2))]
Custom_comb1$Result[,sqrt(mean((volume - pred_9)^2))]
Custom_comb1$Result[,sqrt(mean((volume - pred_10)^2))]
Naive$Result[,sqrt(mean((volume - pred_1)^2))]
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```
```{r, cache = TRUE}
plot(Custom_comb2$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Custom_comb3$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb6$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb7$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb8$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb9$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Custom_comb10$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date])

plot(Custom_comb2$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Custom_comb3$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_comb4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_comb5$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_comb6$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_comb7$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_comb8$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_comb9$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Custom_comb10$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = month(init_date)])

Custom_comb2$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom_comb3$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom_comb4$Result[,sqrt(mean((volume - pred_2)^2))] 
Custom_comb5$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_comb6$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_comb7$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_comb8$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_comb9$Result[,sqrt(mean((volume - pred_2)^2))]
Custom_comb10$Result[,sqrt(mean((volume - pred_2)^2))]
Naive$Result[,sqrt(mean((volume - pred_1)^2))]
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```

## Combining 
```{r}
Factor10_inter1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10,  reg_form = "volume ~ as.factor(hour):as.factor(week)  + as.factor(w_day):as.factor(week) + s(week) + s(month) + season1 + season2 + year", cores = 48)

Factor10_inter2 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10,  reg_form = "volume ~ as.factor(hour):as.factor(month)  + as.factor(w_day):as.factor(week) + s(week) + s(month) + season1 + season2 + year", cores = 48) #Have run

Factor10_inter3 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10,  reg_form = "volume ~ as.factor(hour):as.factor(week)  + as.factor(w_day):as.factor(month) + s(week) + s(month) + season1 + season2 + year", cores = 48) 

Factor10_inter4 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 10,  reg_form = "volume ~ as.factor(hour):as.factor(month)  + as.factor(w_day):as.factor(month) + s(week) + s(month) + season1 + season2 + year", cores = 48) #Have run
```


```{r}
plot(Factor10_inter4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_3)^2)), keyby = init_date])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_4)^2)), keyby = init_date])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_5)^2)), keyby = init_date])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_6)^2)), keyby = init_date])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_7)^2)), keyby = init_date])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_8)^2)), keyby = init_date])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_9)^2)), keyby = init_date])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_10)^2)), keyby = init_date])

lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date])

plot(Factor10_inter4$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_3)^2)), keyby = month(init_date)])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_4)^2)), keyby = month(init_date)])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_5)^2)), keyby = month(init_date)])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_6)^2)), keyby = month(init_date)])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_7)^2)), keyby = month(init_date)])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_8)^2)), keyby = month(init_date)])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_9)^2)), keyby = month(init_date)])
lines(Factor10_inter4$Result[,sqrt(mean((volume - pred_10)^2)), keyby = month(init_date)])
lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = month(init_date)])

Factor10_inter4$Result[,sqrt(mean((volume - pred_2)^2))]
Factor10_inter4$Result[,sqrt(mean((volume - pred_3)^2))] #Best 
Factor10_inter4$Result[,sqrt(mean((volume - pred_4)^2))] 
Factor10_inter4$Result[,sqrt(mean((volume - pred_5)^2))] 
Factor10_inter4$Result[,sqrt(mean((volume - pred_6)^2))]
Factor10_inter4$Result[,sqrt(mean((volume - pred_7)^2))]
Factor10_inter4$Result[,sqrt(mean((volume - pred_8)^2))]
Factor10_inter4$Result[,sqrt(mean((volume - pred_9)^2))]
Factor10_inter4$Result[,sqrt(mean((volume - pred_10)^2))]
Naive$Result[,sqrt(mean((volume - pred_1)^2))]
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```


```{r, eval = FALSE}
Combo1= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):season + as.factor(season) + as.factor(w_day):season + week1 + week2 + month1 + month2 + year")

Combo2= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):season + as.factor(season) + as.factor(w_day):season + week1 + week2 + month + year")

Combo3= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(hour, by = season) + as.factor(season) + as.factor(w_day):season + week1 + week2 + month1 + month2 + year")

Combo4= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):season + as.factor(season) + as.factor(w_day):season + s(week1) + s(week2) + month + year")

Combo5= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year")  #Much slower model and much better!!!!!!!!!!!!!!!!!!!!!!!!!!


Combo5b= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + s(week1) + s(week2) + month + year") 

Combo5c= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(w_day):as.factor(season)+ s(week1) + s(week2) + month + year") 

Combo5d= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                        p_comps = 0,  reg_form = "volume ~ as.factor(hour)+ as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year")  

Combo6= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(month) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year")  

Baseline5= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + month + year")

Baseline_old= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + as.factor(week) + year")

Best = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year")

#Slight problem with prediction of one month for the below model, therefore had to split up and ommit month of 2014-06 predictions. 
#The problem lies with PC2, baseline and PC1 works fine. 
#Best2 = demand_forecast(forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
#                       p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(month) + as.factor(season) + as.factor(w_day):as.factor(season) + #s(week1) + s(week2) + month + year")

#Debug code: 
#forc_start = '2014-06-01'; forc_end = '2014-06-01'; pred_win = 30; pred_lag = 15; train_y = 5; p_comps = 2;  reg_form = "volume ~ as.factor(hour):as.factor(month) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year"

Best2_comb = list()

Best2a = demand_forecast(X_mat, date_demand,forc_start = '2014-02-01', forc_end = '2014-05-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                        p_comps = 2,  reg_form = "volume ~ as.factor(hour):as.factor(month) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year")
#Best2c = demand_forecast(forc_start = '2014-06-01', forc_end = '2014-06-01', pred_win = 30, pred_lag = 15, train_y = 5, 
#                        p_comps = 2,  reg_form = "volume ~ as.factor(hour):as.factor(month) + as.factor(season) + as.factor(w_day):as.factor(season) + #s(week1) + s(week2) + month + year") 
Best2b = demand_forecast(X_mat, date_demand,forc_start = '2014-07-01', forc_end = '2015-05-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                        p_comps = 2,  reg_form = "volume ~ as.factor(hour):as.factor(month) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year")
Best2 = demand_forecast(X_mat, date_demand,forc_start = '2015-06-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                        p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(month) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year")

Best2_comb$Results = rbind(Best2a$Results, Best2b$Results,Best2$Results)
```


```{r, eval = FALSE}
save(Naive, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Naive.Rda')
save(Combo1, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo1.Rda')
save(Combo2, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo2.Rda')
save(Combo3, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo3.Rda')
save(Combo4, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo4.Rda')
save(Combo5, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo5.Rda')
save(Combo6, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo6.Rda')
save(Best, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Best.Rda')
save(Best2_comb, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Best2_comb.Rda')


save(Baseline5, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Baseline5.Rda')
save(Baseline_old, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Baseline_old.Rda')
```

```{r, cache=TRUE}
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo1.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo2.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo3.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo4.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo5.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Combo6.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Best.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Best2.Rda')

load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Baseline5.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Baseline_old.Rda')
```


# Compare combination Models
```{r, cache=TRUE}
plot(Combo5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(1000, 6000))
#lines(Combo1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date],)
#lines(Combo2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date],)
#lines(Combo3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date],)
#lines(Combo4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date],)
lines(Climatology$Result[,sqrt(mean((volume - clima_pred)^2)), keyby = init_date], col = 'orange', lty = 3)

lines(Best$Result[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], col = 'blue', lty = 3)
lines(Best$Result[,sqrt(mean((volume - pred_3)^2)), keyby = init_date], col = 'purple')

#lines(Baseline5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
#lines(Baseline_old$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'green')
#lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'yellow')

plot(Combo1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(1000, 6000))
lines(Combo2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)],)
lines(Combo3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)],)
lines(Combo4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)],) 
lines(Combo5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'green')

lines(Best$Result[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], col = 'red')
lines(Best$Result[,sqrt(mean((volume - pred_3)^2)), keyby = month(init_date)], col = 'purple')

lines(Baseline5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Baseline_old$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
#lines(Naive$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'yellow')

Combo1$Result[,sqrt(mean((volume - pred_1)^2))]
Combo2$Result[,sqrt(mean((volume - pred_1)^2))]
Combo3$Result[,sqrt(mean((volume - pred_1)^2))]
Combo4$Result[,sqrt(mean((volume - pred_1)^2))]
Combo5$Result[,sqrt(mean((volume - pred_1)^2))]
Combo6$Result[,sqrt(mean((volume - pred_1)^2))]
Best$Result[,sqrt(mean((volume - pred_1)^2))]

Best$Result[,sqrt(mean((volume - pred_2)^2))]
Best$Result[,sqrt(mean((volume - pred_3)^2))]
Best$Result[,sqrt(mean((volume - pred_4)^2))]
Best$Result[,sqrt(mean((volume - pred_5)^2))]
Best$Result[,sqrt(mean((volume - pred_6)^2))]
Best$Result[,sqrt(mean((volume - pred_7)^2))]

Baseline5$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline_old$Result[,sqrt(mean((volume - pred_1)^2))]
#Naive$Result[,sqrt(mean((volume - pred_1)^2))]

plot(Combo5$Result[,volume])
lines(Combo5$Result[,volume], col = 'red')

plot(Combo5$Result[year(date) ==2019 & month ==3,volume], cex = 0.4)
#lines(Baseline_old$Result[year(date) ==2019& month ==3,pred_1], col = 'blue')
lines(Combo5$Result[year(date) ==2019& month ==3,pred_1], col = 'brown')
#lines(Best$Result[year(date) ==2019& month ==3,pred_2], col = 'red', lty = 2)
lines(Best$Result[year(date) ==2019& month ==3,pred_3], col = 'purple')

#lines(Naive$Result[year(date) ==2019& month ==3,pred_1], col = 'yellow', lty = 2)

plot(Best$Result[year(date) ==2021,volume -pred_3], col = 'purple', type = 'l')
acf(Best$Result[year(date) ==2021,volume -pred_3])
acf(Best$Result[,volume -pred_3])
```

# Make a temperature plot with 
1) Loss for all years
1) Compare temp for 2016 against mean temp over all year per hour, day
2) Compare predictions from baseline model and best model for 2016
3) Compare volume for that year


Skill by month
Show difference to pure climatology model. 

jensens inequality read up

Instead of doing the squared error directly

we sum the predictions for each day and compared for summed volume. 

the other version has a rational for stake holders



```{r}
prep = prep_demand_temp_data(include_na_volume = FALSE)
#
X_mat = prep$X_mat #Temperature field
date_demand = prep$date_demand
X_mean = rowMeans(X_mat) - 273.15
date_demand[, grid_mean_temp:= X_mean]
date_demand[, climatology:= mean(grid_mean_temp), by = .(hour, yday(date))]
plot(date_demand[year(date)==2016 & hour %in%12,.(date, climatology)], type = 'l', 
     ylim = c(-9, 16), ylab = 'Temperature (°C)', xlab = 'Date', main = 'Daily Mean Grid Temperature at 12:00 (lat 4-25, long 55-75)')
lines(date_demand[year(date)==2016 & hour %in%12,.(date, grid_mean_temp)], col = 'red')
legend('bottomright', lty = 1, cex = 0.7, col = c('red', 'black'), legend = c("2016 observed","Climatology"), title = 'Temperature')

date_demand[, climatology:= mean(grid_mean_temp), by = .(yday(date))]
date_demand[, mm_temp:= mean(mean_temp), by = date]
plot(date_demand[year(date)==2016,.(date, mm_temp)], type = 'l', ylim = c(-8.7, 17))
lines(date_demand[year(date)==2016,.(date, climatology)], col = 'red')

yr = 2016
date_demand[, mean_vol:= mean(volume), by = date]
plot(  date_demand[year(date)==yr & hour %in%12,volume], col = 'black', ylim = c(30000, 65000), pch = 16, cex= 0.6, type = 'l')
lines(Best$Results[year(date)==yr & hour %in%12,pred_3], col = 'red')
lines(Best$Results[year(date)==yr & hour %in%12,pred_1], col = 'blue')

plot(date_demand[year(date)==yr &  wday(date)  %in% c(1) &hour %in%12,volume, by = date], col = 'black', ylim = c(30000, 65000), pch = 16, cex= 0.6, type = 'l')

#Reason for including week-term 
hour_x = 24
plot(date_demand[year(date)==yr &  wday(date)  %in% c(1) &hour %in%hour_x,volume, by = date], col = 'black', ylim = c(25000, 65000), pch = 16, cex= 0.6, type = 'l', main = paste0('Difference between weekdays at ', hour_x, ':00'))
for (i in 2:7){
    lines(date_demand[year(date)==yr &  wday(date)  %in% c(i) &hour %in%hour_x,volume, by = date], col = i)
}

"2014-02-15" "2014-04-15" "2014-06-15" "2014-08-15"
"2014-09-15" "2014-11-15" "2015-01-15" "2015-02-15" "2015-04-15" "2015-06-15"
"2015-08-15" "2015-09-15" "2015-11-15" "2016-01-15" "2016-02-15" "2016-04-15"
"2016-06-15" "2016-08-15" "2016-09-15" "2016-11-15" "2017-01-15" "2017-02-15"
"2017-04-15" "2017-06-15" "2017-08-15" "2017-09-15" "2017-11-15" "2018-01-15"
"2018-02-15" "2018-04-15" "2018-06-15" "2018-08-15" "2018-09-15" "2018-11-15"
"2019-01-15" "2019-02-15" "2019-04-15" "2019-06-15" "2019-08-15" "2019-09-15"
"2019-11-15" "2020-01-15" "2020-02-15" "2020-04-15" "2020-06-15" "2020-08-15"
"2020-09-15" "2020-11-15" "2021-01-15" "2021-02-15" "2021-04-15" "2021-06-15"
"2021-08-15" "2021-09-15"

```

## By lead time
```{r}

```



Spline interaction on pca
```{r}
Best_inter1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year", custom = 's(PC1, by = month) + s(PC2)')
```

```{r}
Best_inter2= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year", custom = 's(PC1, by = as.factor(month)) + s(PC2)')

```

```{r}
Best_inter3 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year", custom = 's(PC1, by = as.factor(season)) + s(PC2)')
```



```{r}
Best_inter4 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year", custom = 's(PC1) + s(PC2) + s(PC5)')
```


```{r}
Best_inter5 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 6,  reg_form = "volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year", custom = 's(PC1) + s(PC2) + s(PC5)')
```


```{r}
Baseline_old$Result[,sqrt(mean((volume - pred_1)^2))]
#Combo1$Result[,sqrt(mean((volume - pred_1)^2))]
#Combo2$Result[,sqrt(mean((volume - pred_1)^2))]
#Combo3$Result[,sqrt(mean((volume - pred_1)^2))]
#Combo4$Result[,sqrt(mean((volume - pred_1)^2))]
#Combo5$Result[,sqrt(mean((volume - pred_1)^2))]
Combo6$Result[,sqrt(mean((volume - pred_1)^2))]
Best$Result[,sqrt(mean((volume - pred_1)^2))]
Best$Result[,sqrt(mean((volume - pred_2)^2))]
Best$Result[,sqrt(mean((volume - pred_3)^2))]
#Best$Result[,sqrt(mean((volume - pred_4)^2))]
#Best$Result[,sqrt(mean((volume - pred_5)^2))]
#Best$Result[,sqrt(mean((volume - pred_6)^2))]
#Best$Result[,sqrt(mean((volume - pred_7)^2))]

#Baseline5$Result[,sqrt(mean((volume - pred_1)^2))]

Best_inter1$Result[,sqrt(mean((volume - pred_2)^2))]
Best_inter2$Result[,sqrt(mean((volume - pred_2)^2))]
Best_inter3$Result[,sqrt(mean((volume - pred_2)^2))]
Best_inter4$Result[,sqrt(mean((volume - pred_2)^2))]
```

Have not run inter_5 yet


# OTHER STUFF


What quality of the PCA are we leveraging?
```{r, eval = FALSE}
Baseline1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + as.factor(month) + year")

Baseline2= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + month1 + month2 + year")

Baseline3= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + year")

Baseline4= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + month1 + month2 + year")

Baseline5= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + month + year")

Baseline6= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ hour1 + hour2 + week1 + week2 + month + year")
```

```{r, eval = FALSE}
plot(Baseline1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l')
lines(Baseline2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Baseline3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'green')
lines(Baseline4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'blue')
lines(Baseline5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')
lines(Baseline6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])

plot(Baseline1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l')
lines(Baseline2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Baseline3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'green')
lines(Baseline4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'blue')
lines(Baseline5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')
lines(Baseline6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])


Baseline1$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline2$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline3$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline4$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline5$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline6$Result[,sqrt(mean((volume - pred_1)^2))]
```

Comparing with 10 training years 
```{r, eval = FALSE}
Baseline1 = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 10, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + as.factor(month) + year")

plot(Baseline1$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l')


plot(Baseline1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l')

Baseline1$Result[,sqrt(mean((volume - pred_1)^2))]


Baseline2= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 10, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + month1 + month2 + year")

plot(Baseline2$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l')


plot(Baseline2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l')

Baseline2$Result[,sqrt(mean((volume - pred_1)^2))]


Baseline3= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 10, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + year")

plot(Baseline3$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l')


plot(Baseline3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l')

Baseline3$Result[,sqrt(mean((volume - pred_1)^2))]

Baseline4= demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 10, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + month1 + month2 + year")
plot(Baseline4$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l')


plot(Baseline4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l')

Baseline4$Result[,sqrt(mean((volume - pred_1)^2))]

Baseline5= demand_forecast(forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 10, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + month + year")
plot(Baseline5$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l')


plot(Baseline5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l')

Baseline5$Result[,sqrt(mean((volume - pred_1)^2))]

Baseline6= demand_forecast(forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 10, 
                    p_comps = 0,  reg_form = "volume ~ hour1 + hour2 + week1 + week2 + month + year")
plot(Baseline6$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l')

plot(Baseline6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l')

Baseline6$Result[,sqrt(mean((volume - pred_1)^2))]

```

```{r, eval = FALSE}
plot(Baseline1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2500, 5000))
lines(Baseline2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Baseline3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'green')
lines(Baseline4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'blue')
lines(Baseline5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')
lines(Baseline6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])

Baseline1$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline2$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline3$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline4$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline5$Result[,sqrt(mean((volume - pred_1)^2))]
Baseline6$Result[,sqrt(mean((volume - pred_1)^2))]

```

5 years of training
[1] 3763.723
[1] 3812.147
[1] 3727.427
[1] 3729.483
[1] 3653.674
3675.659 "volume ~ as.factor(hour) + as.factor(week) + month + year" 5c 5 years
[1] 4088.025

10 years of training
[1] 3836.625
[1] 3876.872
[1] 3792.937
[1] 3795.673
[1] 3719.805
3746.95 "volume ~ as.factor(hour) + as.factor(week) + month + year" 5b 10 years
[1] 4146.292


The best one here is baseline 5 using cosine + sine on the week term. 


```{r, eval = FALSE}
Eight_pca = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 8,  reg_form = "volume ~ as.factor(hour) + as.factor(month) + year")
```


```{r}
plot(Eight_pca$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', col = 'red', ylim = c(0,6000))
lines(Eight_pca$Results[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], col = 2)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_3)^2)), keyby = init_date], col = 3)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_4)^2)), keyby = init_date], col = 4)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_5)^2)), keyby = init_date], col = 5)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_6)^2)), keyby = init_date], col = 6)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_7)^2)), keyby = init_date], col = 7)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_8)^2)), keyby = init_date], col = 8)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_9)^2)), keyby = init_date], col = 9)

plot(Eight_pca$Results[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(0,6000), col = 'red')
cols = colnames(Eight_pca$Results)[grep("^[p].*", colnames(Eight_pca$Results))]

lines(Eight_pca$Results[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], type = 'l', col = 1)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_3)^2)), keyby = month(init_date)], type = 'l', col = 1)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_4)^2)), keyby = month(init_date)], type = 'l', col = 3)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_5)^2)), keyby = month(init_date)], type = 'l', col = 4)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_6)^2)), keyby = month(init_date)], type = 'l', col = 5)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_7)^2)), keyby = month(init_date)], type = 'l', col = 6)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_8)^2)), keyby = month(init_date)], type = 'l', col = 7)
lines(Eight_pca$Results[,sqrt(mean((volume - pred_9)^2)), keyby = month(init_date)], type = 'l', col = 1)



```


```{r, eval = FALSE}
Eight_pca2 = demand_forecast(forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, p_comps = 8,  reg_form = "volume ~ as.factor(hour) + week1 + week2 + month + year")
```


```{r, eval = FALSE}
plot(Eight_pca2$Results[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', col = 'red', ylim = c(0,6000))
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_2)^2)), keyby = init_date], col = 2)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_3)^2)), keyby = init_date], col = 3)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_4)^2)), keyby = init_date], col = 4)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_5)^2)), keyby = init_date], col = 5)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_6)^2)), keyby = init_date], col = 6)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_7)^2)), keyby = init_date], col = 7)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_8)^2)), keyby = init_date], col = 8)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_9)^2)), keyby = init_date], col = 9)

plot(Eight_pca2$Results[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(0,6000), col = 'red')
cols = colnames(Eight_pca2$Results)[grep("^[p].*", colnames(Eight_pca2$Results))]

lines(Eight_pca2$Results[,sqrt(mean((volume - pred_2)^2)), keyby = month(init_date)], type = 'l', col = 1)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_3)^2)), keyby = month(init_date)], type = 'l', col = 1)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_4)^2)), keyby = month(init_date)], type = 'l', col = 3)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_5)^2)), keyby = month(init_date)], type = 'l', col = 4)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_6)^2)), keyby = month(init_date)], type = 'l', col = 5)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_7)^2)), keyby = month(init_date)], type = 'l', col = 6)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_8)^2)), keyby = month(init_date)], type = 'l', col = 7)
lines(Eight_pca2$Results[,sqrt(mean((volume - pred_9)^2)), keyby = month(init_date)], type = 'l', col = 1)



```

```{r, eval = FALSE}
Eight_pca$Results[,sqrt(colMeans((volume -.SD)^2)), .SDcols = grep("^pred", colnames(Eight_pca$Results))]

Eight_pca2$Results[,sqrt(colMeans((volume -.SD)^2)), .SDcols = grep("^pred", colnames(Eight_pca2$Results))]

colMeans(mod_fix$test_RMSE[,1:9])
```

This shows that 
1) the performance of the sincos model Eight_pca2 is better than the factor one.
2) That this is still substantially lower than the same ones from earlier. Why? Is it because we are taking a different average?


```{r, eval = FALSE}
Three_pca = demand_forecast(X_mat, date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 3,  reg_form = "volume ~ as.factor(hour) + as.factor(month) + year")
```


```{r, eval = FALSE}
Three_pca = demand_forecast(X_mat, date_demand,forc_start = '2019-01-01', forc_end = '2019-09-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 3,  reg_form = "volume ~ as.factor(hour) + as.factor(month) + year")
```


## Check if the two datasets are similar
```{r, eval = FALSE}
nc = nc_open("/Users/Eirik/Desktop/Master2023/Data/Prob1_data/era_historical_data.nc4")
X = ncvar_get(nc, "2m_temperature")
hours = 1:24
days = as.Date(ncvar_get(nc, "day"), origin = "1970-01-01")
nc_close(nc)

X_temp = matrix(as.vector(X),
                nrow = dim(X)[3] * dim(X)[4], #hours times days
                ncol = dim(X)[1] * dim(X)[2], #lon time lat
                byrow = TRUE)

dt_date = data.table(expand.grid(hour = hours,date = days))
    
dt_date[, I:= 1:.N]
nc2 = nc_open("/Users/Eirik/Desktop/Master2023/Data/Prob1_data/temperature_data.nc4")
X2 = ncvar_get(nc2, "2m_temperature")
hours2 = 1:24
days2 = as.Date(ncvar_get(nc2, "day"), origin = "1970-01-01")
nc_close(nc2)

X_temp2 = matrix(as.vector(X2),
                nrow = dim(X2)[3] * dim(X2)[4], #hours times days
                ncol = dim(X2)[1] * dim(X2)[2], #lon time lat
                byrow = TRUE)

dt_date2 = data.table(expand.grid(hour = hours2,date = days2))
dt_date2[, I:= 1:.N]
```
