---
title: "Demand Forecasting"
output: html_notebook
---

# Best Baseline Test

This document tries to find the best baseline model to predict the demand volume as part of problem 1 of the thesis. 

Main conclusions: 

1) The best baseline was first the model combo1: 

volume ~ as.factor(hour):as.factor(season) + as.factor(season) + as.factor(w_day):as.factor(season) + s(week1) + s(week2) + month + year

This is the result of a process that first tried to find a combination of the best covariates one by one, and some tinkering. 


2) What we added right at the end here was the season term in addition to using it as an interaction. 
The season term is motivated by the very different pattern in the pc temperature data in terms of daily variations between summer and winter. 
Do we see this in the demand data as well?
This was well motivated and lead to substantive gains in the model. 

Is the over-parametrization a problem? we are using well over 100 parameters to model the relationship. 
Could also involve an AIC-score here just to check the generalizability of the model 
They shouldn't be just a ton of parameters, but they are a ton of parameters that contributes to the performance of the model in a discernible way. 
Modelling hour as a factor contra as a spline of sinusoidal is an empirical question to an extent. 

Compared to the 24*50 with weeks or 24*12 with months parameters might be well to many, might not generalize well and might effect the speed as well. 
This is motivated by the nature of daily variation and its differing function throughout the 4 seasons. 
A lot of the variation comes down to the hourly level, how does this translate to when we only have access to data that are in 6-hour intervals?

3) The best training year is 5 though some tweaking can be done to ascertain this. 


4) Issues with regard to the presentation is that: 
a) Are we really supposed to choose based on CV? 
b) Some of the differences here are fairly minimal. Should we experiment with model averaging?
c) Should model averaging come into play at a later stage?
d) Should I try all combinations here and see which is best or is the more informed piecemeal approach better?

5) Other tests should be moved to another markdown document for summary. 

6) We also run one model with 2PC which performs with a skill score of 0.17 which is very well indeed, higher I think 

7) Might also check how the performance is affected by each term in the formula, I bet that the lone factor seasonal term will not contribute much, nor the daily, but we can see, with PCs I guess. 

8) Is 2 PCs still the best?




1) Set-up
```{r, cache=TRUE}
#ssh eirikhsj@nam-shub-01.uio.no

#module load  R/4.2.0-foss-2021b
#install.packages('DemandForecast', repos = NULL,type = "source")
library(DemandForecast)

if(file.exists("~/Desktop/Master2023/Data/")){
    prep = prep_demand_temp_data(include_na_volume = FALSE, 
                          path = "~/Desktop/Master2023/Data/")
}else{
    prep = prep_demand_temp_data(include_na_volume = FALSE)
}

#
X_mat = prep$X_mat #Temperature field
date_demand = prep$date_demand
#dt_date = prep$dt_date
#dt_unified = merge(dt_demand, dt_date, by = c("date", "hour"))

#Specify time covariates
date_demand[,week:= week(date)]
date_demand[,week1 :=  round(cos(2*pi * week/52), digits = 7) ]
date_demand[,week2 :=  round(sin(2*pi * week/52), digits = 7) ]

date_demand[,month:= month(date)]
date_demand[,month1 := round(cos(2*pi * month/12), digits = 7)]
date_demand[,month2 := round(sin(2*pi * month/12), digits = 7)]

date_demand[,hour1 := cos(2*pi * hour/24) ]
date_demand[,hour2 := sin(2*pi * hour/24) ]

date_demand[,year:= year(date)]

date_demand[,w_day:= as.numeric(format(date, "%u"))]
date_demand[,w_day1 := cos(2*pi * w_day/7) ]
date_demand[,w_day2 := sin(2*pi * w_day/7) ]

date_demand[,season:= ifelse(month(date) %in% c(12,1,2), 1, 
                            ifelse(month(date) %in% c(3,4,5), 2,
                            ifelse(month(date) %in% c(6,7,8), 3, 4)))]

date_demand[,season1 := round(cos(2*pi * season/4), digits = 7)]
date_demand[,season2 := round(sin(2*pi * season/4), digits = 7)]

date_demand[,hourly_mean_grid := rowMeans(X_mat)]

# forc_start = '2016-01-01'; forc_end = '2023-01-01'; pred_win = 30; pred_lag = 15; train_y = 5;
# p_comps = 0;  reg_form = "volume ~ as.factor(hour) + as.factor(month) + year"; custom = FALSE; incl_climatology=FALSE; cores = 8
```

Best baseline:

How should we find the best baseline?
First look at which of the 4 configurations of each of the 5 time covariates perform best. So use these in combination before tweaking. 

We have a simple continuous, spline, as.factor(), and sinusoidal. 
# 1) Climatology
```{r}
Climatology = demand_forecast(forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5,
                              p_comps = 0,  reg_form = "volume ~ 1", incl_climatology = TRUE, custom = FALSE,
                              X_mat=X_mat, date_demand = date_demand, cores = 4)
```



# 2) Single covariates
```{r, eval = FALSE}
Year1 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', 
            pred_win = 30, pred_lag = 15, train_y = 5, p_comps = 0,  reg_form = "volume ~ year", incl_climatology = FALSE)
Year2 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', 
            pred_win = 30, pred_lag = 15, train_y = 5, p_comps = 0,  reg_form = "volume ~ as.factor(year)", incl_climatology = FALSE)
```

```{r, eval = FALSE}
Season1 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ season", incl_climatology = FALSE)
Season2 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(season)", incl_climatology = FALSE)
Season3 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ season1 + season2", incl_climatology = FALSE)
Season4 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(season, bs = 'cc', k = 4)", incl_climatology = FALSE)
```


```{r, eval = FALSE}
Wday1 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ w_day", incl_climatology = FALSE)
Wday2 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(w_day)", incl_climatology = FALSE)
Wday3 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ w_day1 + w_day2", incl_climatology = FALSE)
Wday4 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(w_day, bs = 'cc', k = 7)", incl_climatology = FALSE)
#Interaction

Wday5 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(w_day, by = season, bs = 'cc', k = 7) ", incl_climatology = FALSE)
Wday6 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(w_day, by = month, bs = 'cc', k = 7) ", incl_climatology = FALSE)
Wday7 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(w_day, by = week, bs = 'cc', k = 7) ", incl_climatology = FALSE)

Wday8 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(w_day):as.factor(season)", incl_climatology = FALSE)
Wday9 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(w_day):as.factor(month)", incl_climatology = FALSE)
Wday10 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(w_day):as.factor(week)", incl_climatology = FALSE)
```


```{r, eval = FALSE}
Week1 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ week")
Week2 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(week)")
Week3 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(week)")
Week4 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ week1 + week2")

#Interactions
Week5 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ week1:season + week2:season")
Week6 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(week1, by = season) + s(week2, by = season)")
```


```{r, eval = FALSE}
Month1 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ month")
Month2 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(month)")
Month3 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(month)")
Month4 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ month1 + month2")
#Interactions
Month5 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(month, by = season)")  
Month6 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(month, bs = 'cc', k = 12)")  

```

```{r, eval = FALSE}
Hour1 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ hour")
Hour2 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(hour)")
Hour3 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour)")  #Best
Hour4 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ hour1 + hour2")
#Interactions
Hour5 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(hour, by = season)")
Hour6 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(hour, by = month)")
Hour7 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ s(hour, by = week)")
Hour8 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(season)")
Hour9 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(month)")
Hour10 = demand_forecast(X_mat,date_demand,forc_start = '2016-01-01', forc_end = '2023-01-01', pred_win = 30, pred_lag = 15, train_y = 5, 
                    p_comps = 0,  reg_form = "volume ~ as.factor(hour):as.factor(week)")
```

### Save models
```{r, eval = FALSE}
save(Hour1, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour1.Rda')
save(Hour2, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour2.Rda')
save(Hour3, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour3.Rda')
save(Hour4, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour4.Rda')
save(Hour5, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour5.Rda')
save(Hour6, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour6.Rda')
save(Hour7, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour7.Rda')
save(Hour8, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour8.Rda')
save(Hour9, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour9.Rda')
save(Hour10, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour10.Rda')

save(Week1, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week1.Rda')
save(Week2, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week2.Rda')
save(Week3, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week3.Rda')
save(Week4, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week4.Rda')
save(Week5, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week5.Rda')
save(Week6, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week6.Rda')
save(Week7, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week7.Rda')

save(Month1, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month1.Rda')
save(Month2, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month2.Rda')
save(Month3, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month3.Rda')
save(Month4, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month4.Rda')
save(Month5, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month5.Rda')
save(Month6, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month6.Rda')
save(Month7, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month6.Rda')

save(Year1, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Year1.Rda')
save(Year2, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Year2.Rda')

save(Wday1, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday1.Rda')
save(Wday2, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday2.Rda')
save(Wday3, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday3.Rda')
save(Wday4, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday4.Rda')
save(Wday5, file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday5.Rda')

```

```{r, cache = TRUE}
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour1.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour2.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour3.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour4.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour5.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour6.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour7.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour8.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour9.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Hour10.Rda')

load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week1.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week2.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week3.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week4.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week5.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week6.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Week7.Rda')

load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month1.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month2.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month3.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month4.Rda')
#load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month5.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month6.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Month7.Rda')

load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Year1.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Year2.Rda')

load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday1.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday2.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday3.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday4.Rda')
load(file = '/Users/Eirik/Desktop/Master2023/Output_data/output_demand_forecast_best_baseline/Wday5.Rda')

```



# 3) Compare results Single Covariates

Here we first find that the factor version is the best one, but we can also observe a strong difference in how the temperature shifts by the hour in winter and summertime, this led us to try some interactions to look at if the hour term was seasonally different. 
And having tried interactions with week, month, and season, the latter was found to be the best. 
```{r, cache = TRUE}
plot(Hour1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(Hour2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour7$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour8$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour9$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Hour10$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Climatology$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'blue')

plot(Hour1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(Hour2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour7$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour8$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour9$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Hour10$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])

Hour1$Result[,sqrt(mean((volume - pred_1)^2))]
Hour2$Result[,sqrt(mean((volume - pred_1)^2))]
Hour3$Result[,sqrt(mean((volume - pred_1)^2))] 
Hour4$Result[,sqrt(mean((volume - pred_1)^2))]
Hour5$Result[,sqrt(mean((volume - pred_1)^2))]
Hour6$Result[,sqrt(mean((volume - pred_1)^2))] 
Hour7$Result[,sqrt(mean((volume - pred_1)^2))]
Hour8$Result[,sqrt(mean((volume - pred_1)^2))]
Hour9$Result[,sqrt(mean((volume - pred_1)^2))]
Hour10$Result[,sqrt(mean((volume - pred_1)^2))] #Best as.factor(hour):as.factor(month)
Climatology$Result[,sqrt(mean((volume - clima_pred)^2))]
```

## Looking at week
The success with adding an interaction was not repeated
```{r, cache = TRUE}
plot(Week1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(Week2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Week3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Week4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')
lines(Week5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Week6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])

plot(Week1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(Week2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Week3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Week4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')
lines(Week5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Week6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])

Week1$Result[,sqrt(mean((volume - pred_1)^2))]
Week2$Result[,sqrt(mean((volume - pred_1)^2))] #Best s(week)
Week3$Result[,sqrt(mean((volume - pred_1)^2))] 
Week4$Result[,sqrt(mean((volume - pred_1)^2))] # week1 + week2
Week5$Result[,sqrt(mean((volume - pred_1)^2))]
Week6$Result[,sqrt(mean((volume - pred_1)^2))] 
```

## Looking at season
```{r, cache = TRUE}
plot(Season1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(Season2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Season3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Season4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')


plot(Season1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(Season2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Season3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Season4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')


Season1$Result[,sqrt(mean((volume - pred_1)^2))]
Season2$Result[,sqrt(mean((volume - pred_1)^2))]
Season3$Result[,sqrt(mean((volume - pred_1)^2))] 
Season4$Result[,sqrt(mean((volume - pred_1)^2))]
```

## Looking at week_day
The success with adding an interaction was found again here, there is some
```{r, cache = TRUE}
plot(Wday1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(Wday2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Wday3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Wday4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')
lines(Wday5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Wday6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')
lines(Wday7$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Wday8$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Wday9$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Wday10$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])

plot(Wday1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(Wday2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Wday3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Wday4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')
lines(Wday5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Wday6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Wday7$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Wday8$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Wday9$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Wday10$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])

Wday1$Result[,sqrt(mean((volume - pred_1)^2))]
Wday2$Result[,sqrt(mean((volume - pred_1)^2))]
Wday3$Result[,sqrt(mean((volume - pred_1)^2))] 
Wday4$Result[,sqrt(mean((volume - pred_1)^2))]
Wday5$Result[,sqrt(mean((volume - pred_1)^2))] #Best as.factor(w_day):season
Wday6$Result[,sqrt(mean((volume - pred_1)^2))]
Wday7$Result[,sqrt(mean((volume - pred_1)^2))]
Wday8$Result[,sqrt(mean((volume - pred_1)^2))]
Wday9$Result[,sqrt(mean((volume - pred_1)^2))]
Wday10$Result[,sqrt(mean((volume - pred_1)^2))]
```
## Looking at Year
```{r, cache = TRUE}
plot(Year1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Year2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])

plot(Year1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700), col = 'red')
lines(Year2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])

Year1$Result[,sqrt(mean((volume - pred_1)^2))] #Best
Year2$Result[,sqrt(mean((volume - pred_1)^2))]
```

## Month

The best is the sinusoidal model
```{r, cache = TRUE}
plot(Month1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], type = 'l', ylim = c(2000, 13700))
lines(Month2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Month3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Month4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date], col = 'red')
lines(Month5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])
lines(Month6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = init_date])

plot(Month1$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], type = 'l', ylim = c(2000, 13700))
lines(Month2$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Month3$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Month4$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)], col = 'red')
lines(Month5$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])
lines(Month6$Result[,sqrt(mean((volume - pred_1)^2)), keyby = month(init_date)])

Month1$Result[,sqrt(mean((volume - pred_1)^2))]
Month2$Result[,sqrt(mean((volume - pred_1)^2))]
Month3$Result[,sqrt(mean((volume - pred_1)^2))] 
Month4$Result[,sqrt(mean((volume - pred_1)^2))] # Best volume ~ month1 + month2"
Month5$Result[,sqrt(mean((volume - pred_1)^2))]
Month6$Result[,sqrt(mean((volume - pred_1)^2))] 
```

