---
title: "Final Article Run"
output: html_document
date: "2024-01-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Running Models for Energy Article

This document describes all the final model runs made for the Energy Demand Article based on the master thesis Energy Demand Forecasting.



In this document we present to main categories of models: 
First: Energy Demand Models that utilizes temperature and time information. 
Second: Temperature Forecasting Models that utilize NWP seasonal forecasts. 


## Load Data
First we load the desired data for the Energy Demand Models. We need the demand data and the temperature data, both provided by the prep_demand_temp_data() function. The reference PC_ERA data is needed for the NWP data. 

```{r Load, include=TRUE}
    
library(DemandForecast)

##### 1. Get demand volume and ERA observed temperature data #################
PATH = "/nr/samba/user/esjavik/EnergyDemandData/"

MODPATH = "/nr/samba/user/esjavik/DemandModels/"

prep = prep_demand_temp_data(include_na_volume = "Some", path = PATH) #Include NA to get pre-trained
#
X_mat = prep$X_mat #Temperature field
date_demand = prep$date_demand


##### 2. Get PC of ERA observed temperature data #################
if (file.exists(paste0(MODPATH,'PC_ERA_79_92.Rda'))){
  print('File exists - Loading file')
  load(paste0(MODPATH,'PC_ERA_79_92_23.Rda'))
} else {
  print('File does NOT exists - Creating file')
  PC_ERA = get_pre_trained_PC_ERA(file=PATH, X_mat,date_demand= date_demand,
                                  start_train = "1979-01-01", stop_train="1992-12-31", start_test = "1993-01-01", stop_test="2023-12-31",
                                  NWP=NA,run_again =TRUE)
  save(PC_ERA, file = paste0(MODPATH,'PC_ERA_79_92_23.Rda'))
}
```


## Basic Models
We first start by assessing the quality of the PC-GAM model framework by contrasting it with other frameworks. 

### Climatology
The first contrast model is the climatology model. Here we use 3 years of training data 

```{r Climatology, include=TRUE}

```


### Models with only Time Information
A lot of choices has to be made in order to choose which models to be run. 
We start by using 3 years of training data, a reduced grid (i.e. we cut out some parts of northern Scandinavia), we use simple non-interaction time covariates, and we use no time information. 


```{r inter, include=TRUE}

Complete_Grid_no_int_no_pc = demand_forecast(X_mat[,], date_demand, forc_start = '2016-01-01', forc_end = '2023-12-01',
                                                    pred_win = 31, pred_lag = 0, train_y = 3, p_comps = 0, no_pc = TRUE, incl_climatology = TRUE,
                                                    reg_form = "volume~ as.factor(hour) + as.factor(w_day) + as.factor(month) + as.factor(season) + as.factor(week) + year" ,
                                                    cores = 10, custom = FALSE, Setup = "Rolling")



Small_Grid_no_int_no_pc = demand_forecast(X_mat[,1:220], date_demand, forc_start = '2016-01-01', forc_end = '2023-12-01',
                                                    pred_win = 31, pred_lag = 0, train_y = 3, p_comps = 0, no_pc = TRUE, incl_climatology = TRUE,
                                                    reg_form = "volume~ as.factor(hour) + as.factor(w_day) + as.factor(month) + as.factor(season) + as.factor(week) + year" ,
                                                    cores = 10, custom = FALSE, Setup = "Rolling")
```



```{r inter, include=TRUE}

Small_Grid_all_int_no_pc = demand_forecast(X_mat[,1:220], date_demand, forc_start = '2016-01-01', forc_end = '2023-12-01',
                                                    pred_win = 31, pred_lag = 0, train_y = 3, p_comps = 0, no_pc = TRUE, incl_climatology = TRUE,
                                                    reg_form = "volume~ as.factor(hour) + as.factor(w_day) + as.factor(month) + as.factor(season) + as.factor(week) + year + as.factor(w_day):as.factor(month)+as.factor(hour):as.factor(week) + as.factor(hour):as.factor(w_day) " ,
                                                    cores = 10, custom = FALSE, Setup = "Rolling")
```




### Mean Grid Model
```{r Mean_Grid, include=TRUE}

Small_Grid_all_int_no_pc = demand_forecast(X_mat[,1:220], date_demand, forc_start = '2016-01-01', forc_end = '2023-12-01',
                                                    pred_win = 31, pred_lag = 0, train_y = 3, p_comps = 0, no_pc = TRUE, incl_climatology = TRUE,
                                                    reg_form = "volume~ as.factor(hour) + as.factor(w_day) + as.factor(month) + as.factor(season) + as.factor(week) + year + as.factor(w_day):as.factor(month)+as.factor(hour):as.factor(week) + as.factor(hour):as.factor(w_day) " ,
                                                    cores = 10, custom = FALSE, Setup = "Rolling")
```



### PC Temperature Models
```{r PC_Models, include=TRUE}

Small_Grid_all_int_PC_1_10 = demand_forecast(X_mat[,1:220], date_demand, forc_start = '2016-01-01', forc_end = '2023-12-01',
                                                    pred_win = 31, pred_lag = 0, train_y = 3, p_comps = 10, no_pc = TRUE, incl_climatology = TRUE,
                                                    reg_form = "volume~ as.factor(hour) + as.factor(w_day) + as.factor(month) + as.factor(season) + as.factor(week) + year + as.factor(w_day):as.factor(month)+as.factor(hour):as.factor(week) + as.factor(hour):as.factor(w_day) " ,
                                                    cores = 10, custom = FALSE, Setup = "Rolling")

load("Small_Grid_all_int_PC_1_10.Rda")

Small_Grid_all_int_PC_1_10$Results[!is.na(volume) & year(date) == 2023,lapply(.SD, function(x) {sqrt(mean((volume-x)**2))}), .SDcols = paste0('pred_', seq(1:11))]
Small_Grid_all_int_PC_1_10$Results[!is.na(volume) ,lapply(.SD, function(x) {sqrt(mean((volume-x)**2))}), .SDcols = paste0('pred_', seq(1:4)), by = .(month(date), year(date))]

```

The surprising thing here is the very poor performance for the PC1+2 model for 2023, we would have had a better model if we had modelled especially months 8-9-10-11 better. We try below with the old grid

```{r inter, include=TRUE}

Complete_Grid_all_int_PC_1_3 = demand_forecast(X_mat[,], date_demand, forc_start = '2016-01-01', forc_end = '2023-12-01',
                                                    pred_win = 31, pred_lag = 0, train_y = 3, p_comps = 3, no_pc = TRUE, incl_climatology = TRUE,
                                                    reg_form = "volume~ as.factor(hour) + as.factor(w_day) + as.factor(month) + as.factor(season) + as.factor(week) + year + as.factor(w_day):as.factor(month)+as.factor(hour):as.factor(week) + as.factor(hour):as.factor(w_day) " ,
                                                    cores = 10, custom = FALSE, Setup = "Rolling")


Complete_Grid_all_int_PC_1_3$Results[!is.na(volume) & year(date) == 2023,lapply(.SD, function(x) {sqrt(mean((volume-x)**2))}), .SDcols = paste0('pred_', seq(1:11))]
Complete_Grid_all_int_PC_1_3$Results[!is.na(volume) ,lapply(.SD, function(x) {sqrt(mean((volume-x)**2))}), .SDcols = paste0('pred_', seq(1:4)), by = .(month(date), year(date))]
```


forc_start = '2016-01-01'; forc_end = '2016-05-01';
                                                    pred_win = 31; pred_lag = 0; train_y = 3; p_comps = 2; no_pc = TRUE; incl_climatology = FALSE;
                                                    reg_form = "volume~ as.factor(hour) + as.factor(w_day) + as.factor(month) + as.factor(season) + as.factor(week) 
                                                    + year + as.factor(w_day):as.factor(month)+as.factor(hour):as.factor(week) + as.factor(hour):as.factor(w_day) " ;
                                                    cores = 1; custom = FALSE; Setup = "Rolling"


### Contrast Models
The contrast models are included to see if there are any modifications to be done with regard to the basic set-up. 

Changing grid size
```{r PC_Models, include=TRUE}

```
Changing training years
```{r PC_Models, include=TRUE}

```
Special Days
```{r PC_Models, include=TRUE}

```


## Performance of Demand Models



## Different Temperature Inputs

Having found a good structural demand model we now turn toward the question of how 
How do we utilize temperature? 

There are 4 different ways: 
1) We use the climatology input 


```{r PC_Models, include=TRUE}
Ensemble_Full_Grid_PC1 = demand_forecast_final(X_mat = X_mat, date_demand = date_demand,forc_start ='2016-01-01', p_comps = 1,
                                 forc_end = '2023-12-01', 
                                 reg_form = "volume ~ as.factor(hour) + as.factor(w_day) + as.factor(week) + as.factor(month) + as.factor(season) + year + as.factor(w_day):as.factor(month) +as.factor(hour):as.factor(week) + as.factor(hour):as.factor(w_day)",
                                 custom = "s(PC1)",cores = 12, setup = "Rolling_final_ensemble")
save(Ensemble_Full_Grid_PC1, file = "~/DemandModelsFinal/Ensemble_Full_Grid_PC1.Rda")


Ensemble_Small_Grid_PC1 = demand_forecast_final(X_mat = X_mat[,1:220], date_demand = date_demand,forc_start ='2016-01-01',p_comps = 1,
                                 forc_end = '2023-12-01', 
                                 reg_form = "volume ~ as.factor(hour) + as.factor(w_day) + as.factor(week) + as.factor(month) + as.factor(season) + year + as.factor(w_day):as.factor(month) +as.factor(hour):as.factor(week) + as.factor(hour):as.factor(w_day)",
                                 custom = "s(PC1)",cores = 12, setup = "Rolling_final_ensemble")
save(Ensemble_Small_Grid_PC1, file = "~/DemandModelsFinal/Ensemble_Small_Grid_PC1.Rda")

```






#### Seasonal forecasting
```{r Re-weight Data Creation, include=TRUE}
a = Sys.time()
NWP_quant_rew_simple_25_1993_2023_12 = get_all_NWP_quantiles(path = "/nr/samba/user/esjavik//bigdisk3/pro/sfe_daily_nordic_temperature/",
                                                            pattern = 'sfe_nordic_temperature_',
                                                            start_month  = '01',
                                                            start_year = 1993,
                                                            forc_months = 372,
                                                            PC_ERA_path = "/nr/samba/user/esjavik/DemandModels/PC_ERA_79_92_23.Rda",
                                                            pc_comp = 1,
                                                            reweight = TRUE,
                                                            rew_int =c(15, 1),
                                                            rew_type ='get_simple_weights')
print( Sys.time()-a)

a = Sys.time()
NWP_quant_rew_beta_25_1993_2023_12 = get_all_NWP_quantiles(path = "/nr/samba/user/esjavik//bigdisk3/pro/sfe_daily_nordic_temperature/",
                                                    pattern = 'sfe_nordic_temperature_',
                                                    start_month  = '01', 
                                                    start_year = 1993, 
                                                    forc_months = 372,
                                                    PC_ERA_path = "/nr/samba/user/esjavik/DemandModels/PC_ERA_79_92_23.Rda",
                                                    pc_comp = 1,
                                                    reweight = TRUE, 
                                                    rew_int =c(15, 1), 
                                                    rew_type = 'get_beta_weights') 
print( Sys.time()-a)

a = Sys.time()                                                                                          
NWP_quant_rew_beta_25_1993_2023_12_2 = get_all_NWP_quantiles(path = "/nr/samba/user/esjavik//bigdisk3/pro/sfe_daily_nordic_temperature/",
                                                    pattern = 'sfe_nordic_temperature_',
                                                    start_month  = '01', start_year = 1993, forc_months = 372,
                                                    PC_ERA_path = "/nr/samba/user/esjavik/DemandModels/PC_ERA_79_92_23.Rda",
                                                    pc_comp = 1,                                                            
                                                    reweight = TRUE, 
                                                    rew_int =c(15, 2), 
                                                    rew_type = 'get_beta_weights') 
print( Sys.time()-a)
save(NWP_quant_rew_beta_25_1993_2023_12_2, file = "~/DemandModelsFinal/NWP_quant_rew_beta_25_1993_2023_12_2.Rda")


```

